### 2019-11-15 article.tex
first commit

%\documentclass[conference]{IEEEtran}
\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{url}
\usepackage{listings}
\usepackage{courier}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{blindtext}

%\newcommand{\sd}[1]{\textbf{"\textsc{SD:}} \textit{#1}"}

\newcommand{\nnbb}[2]{
    \fbox{\bfseries\sffamily\scriptsize#1}
    {\sf\small$\blacktriangleright$\textit{#2}$\blacktriangleleft$}
   }
\newcommand{\sd}[1]{\nnbb{\textcolor{orange}{St\'{e}f}}{\textcolor{orange}{#1}\xspace}}
\newcommand{\hr}[1]{\nnbb{Henrique}{#1\xspace}}
\newcommand{\ap}[1]{\nnbb{\textcolor{blue}{Apierr}}{\textcolor{blue}{#1}\xspace}}
\newcommand{\Miner}[0]{Miner\xspace}
\newcommand{\Miners}[0]{Miners\xspace}
\newcommand{\miner}[0]{miner\xspace}
\newcommand{\miners}[0]{miners\xspace}
\newcommand{\gas}[0]{gas\xspace}
\newcommand{\Gas}[0]{Gas\xspace}
\newcommand{\Transaction}[0]{Transaction\xspace}

\newcommand{\SmartGas }[0]{\textsc{SmartGas}\xspace}

\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\etal}{\emph{et al.,}\xspace}
\newcommand{\ct}[1]{{\textsf{#1}}\xspace}
\usepackage[scaled=0.85]{helvet}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Toward  maintainance of  a commencial software: Defects model }
% \title{Toward  maintainance of  a commencial software: Time serie model of defects }
%\thanks{Identify applicable funding agency here. If none, delete this.}}

\author{\IEEEauthorblockN{HOUEKPETODJI Mahugnon Honore\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
Nicolas Anquetil\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Lille, France}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Inria Lille - Nord Europe, France}
homahugnon@gmail.com, nicolas.anquetil@inria.fr}

\maketitle

\begin{abstract}
Legacy systems are old software that style does useful tasks. In industrial software companies, legacy systems are often crucial for the company business model and represent a longterm business investment. Legacy systems are known to be hard to maintain. This is the case in a french company whose main product is twenty years old software written in PowerBuilder (we call it SPB).  Our longterm goal is to help reengineer. But how to validate our intervention? Using moving average, and regression, we evaluate the maintenance state of SPB and produce a dashboard to monitor our future actions. We validate our results with the developer team. We  In this paper, we present a lightweight defects model to help planning commercial software maintenance
\end{abstract}

\begin{IEEEkeywords}
Lagacy system, Defect model .
\end{IEEEkeywords}

\section{Introduction}
Software companies usually invest time and energy to improve the quality of the software they develop to respond to the rising market demands. Features are developed in a hurry sometimes.  As results, they less allow resources for software refactoring to remove source code defects.   As the software is out of control and it becomes hard to improve or maintain. Rewriting this software require time and a lot of resources. At this point, one of the solutions is to reverse-engineer them.

The main business product is SPB of our company. Our longterm goal is to reverse-engineer SPB.  With over 3,000,000 lines of codes, continually updated for more than 20 years,  SPB is not versioned and not unit tested. Bugs is registered in a database without correlation with which part of the system is responsible for the bug. Old versions of SPB are lost until 2012. The original developers of SPB are part of the developers' team. So the currents developers only know SPB partially.  So we could not completely rely on developers view of the system. Besides, there is also a misunderstanding between developer team and the business team. As the business team doesn't know the state of SPB.  In this condition, it is completely impossible to successfully reengineer SPB without  15 years of the useful data model and our analytics.

Our data model and analytics have to the main goal. It provides a report on the state of SPB to the entire company and shows the business team the need to reengineer  SPB. Furthermore, it will help us to monitor our future task on SPB.  In this paper, we will present the data model and the analytics we made.

This paper is structured as follow:

\section{Related Work}\label{sec:related-work}

\section{Background}\label{sec:background}
\subsection{Presentation of SPB}
SPB is build with PowerBuilder. PowerBuilder is an enterprise development tool that allows you to build many types of applications and components. A powerBuilder application components are grouped by libraries.   A PowerBuilder library contains differents type of Objects: Datawindow, User object, Global function, etc.    In SPB libraries  can be grouped by business module . Figure  \ref{fig:pbArchitecture} give an overview of SPB achitecture.
\begin{figure*}[!ht]
    \centering
    {\includegraphics[width=0.9\linewidth]{images/pbArchitecture.jpg}}
    \caption{Simplified SPB achitecture.
Very simplified architecture of SPB}\label{fig:pbArchitecture}
 \end{figure*} 
\subsection{Ticket}
A ticket is related do a task to do.  This task can be fixing a bug, writing documentation, adding a new feature, etc.  A ticket is open for a task . Once the task is done and validated, the ticket is close. A ticket has the following characteristics:
\begin{itemize}
\item the libraries it  is related to
\item the creation date
\item the closing date
\item time spent by a developer
\begin{itemize}
\item time to analyze
\item time to implement solution
\item time to test
\end{itemize}
\item  the estimation of the time needed by the developer to work on the ticket
\end{itemize}

\section{Methodology}\label{sec:methodology}
We collected data  from the company Tickets database .  Then we procced to data cleaning.
The data analytics process is guided by the following research rule:
\begin{itemize}
\item Pose problem
\item Make experimentations on data
\item Validation of results
\end{itemize}
\subsection{Data collection and data cleaning}
The ticket database contains data from 1998  until 2019.  This data includes tickets  differents teams and softwares in  the company. In the field related to the  library a ticket is related to,  the name of the library is not always well written.

  The  datas are consistent  from 2004 to 2019 . We  remove all tickets, non related  to SPB and reformat durations per ticket. By inteviewing developers, we categorize tickets into to sets: tickets related to defects and tickets related two evolutions.

 \subsection{Problems}
 \begin{itemize}
 \item  Is  there a correlation between defects and evolutions per libraries:
 \begin{itemize}
 \item Does evolutions cause defect?
 \item  Does evolutions occur after defects occur?
 \end{itemize}
 \item Is there a relationship between defects  and libraries:
 \begin{itemize}
 \item Does defects in a librarie cause defect in other libraries?
 \item Does some libraries always have defects together?
 \end{itemize}
 \item How long in average does it take to open and close a ticket?
 \item How long in average  does a developer spend on a ticket ?
 \item How long in average does a developer spend to test a ticket after development ?
 \item Does the team manager estimate well  the time needed by the developer?
 \item If the time estimated by the team manager is good, does the developer finish because  of time constraint?
 \end{itemize}

 \subsection{Experimentations}
For each problem, we experiement on the ticket database. 
 \subsubsection{Correlation between defects }
We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolutions.  According to  the visualizations, some libraries trends to as many defects as  evolution over time. For some libraries, we observe that they do not have defects. Some others seem to  have defects after evolution. 
 \section{Results and Discussion}\label{sec:results-discussion}

\section{Summary and Conclusions}\label{sec:conclusion}

%\bibliographystyle{IEEEtran}
\bibliographystyle{alpha}
\bibliography{rmod,others,new}

\vspace{12pt}
\end{document}

### 2019-11-15 article.tex
improve the introduction

@@
 
-\title{Toward  maintainance of  a commencial software: Defects model }
+\title{Toward  maintainance of  a commencial software: Defects model  using moving average and regression}
 % \title{Toward  maintainance of  a commencial software: Time serie model of defects }
@@
 Features are developed in a hurry sometimes.
-As results, they less allow resources for software refactoring to remove source code defects.
-As the software is out of control and it becomes hard to improve or maintain.
+As results, they  allow less resources for software refactoring to remove source code defects.
+As the software grows,  it becomes hard to improve or maintain.
 Rewriting this software require time and a lot of resources.
 At this point, one of the solutions is to reverse-engineer them.
+This is the situation in a French company which main business product is SPB.
 
-The main business product is SPB of our company.
-Our longterm goal is to reverse-engineer SPB.
 With over 3,000,000 lines of codes, continually updated for more than 20 years,  SPB is not versioned and not unit tested.
-Bugs is registered in a database without correlation with which part of the system is responsible for the bug.
+Defects  are registered in a database without correlation with which part of the system is responsible for the bug.
 Old versions of SPB are lost until 2012.
@@
 As the business team doesn't know the state of SPB.
-In this condition, it is completely impossible to successfully reengineer SPB without  15 years of the useful data model and our analytics.
-
-Our data model and analytics have to the main goal.
-It provides a report on the state of SPB to the entire company and shows the business team the need to reengineer  SPB.
-Furthermore, it will help us to monitor our future task on SPB.
-In this paper, we will present the data model and the analytics we made.
-
-This paper is structured as follow:
+Our purpose is:
+\begin{itemize}
+\item How to provides a report on the state of SPB to the entire company?
+\item How to monitor our reverse-engineering task?
+\end{itemize}
+We use defect model and analytics to overcome our problems.
+This paper is structured as follows: we start we related works in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present our defect model.
+In the section 4 we present our results and validation.
+We  conclude in section 5
 
@@
 
-\section{Background}\label{sec:background}
+\section{Defect Model}\label{sec:defectModel}
+\subsection{Moving average}
+A moving average is a statistic technic usually used to smooth a time serie data.
+The principle is to calculate the average of a certain number according to one by one time series values to reflect the numerical trend.
+\begin{equation*} SMA_{n}=\frac{1}{n}\sum\nolimits_{t=k-n+1}^{k}A_{t}\tag{1} \end{equation*}
 \subsection{Presentation of SPB}
-SPB is build with PowerBuilder.
-PowerBuilder is an enterprise development tool that allows you to build many types of applications and components.
-A powerBuilder application components are grouped by libraries.
-A PowerBuilder library contains differents type of Objects: Datawindow, User object, Global function, etc.
-In SPB libraries  can be grouped by business module .
+SPB is  a 3,000,000 PowerBuilder project, developed for more than 20 years.
+SPB is now maintained by a team of 15 developers.
+SPB includes 120 Powerbuilder libraries.
+SPB libraries  is be grouped by business module .
 Figure  \ref{fig:pbArchitecture} give an overview of SPB achitecture.
@@
 A ticket is related do a task to do.
-This task can be fixing a bug, writing documentation, adding a new feature, etc.
+This task can be fixing a defect, writing documentation, adding a new feature, etc.
 A ticket is open for a task .
@@
 \begin{itemize}
-\item Pose problem
+\item Pose a problem
 \item Make experimentations on data
@@
  \begin{itemize}
- \item  Is  there a correlation between defects and evolutions per libraries:
- \begin{itemize}
- \item Does evolutions cause defect?
- \item  Does evolutions occur after defects occur?
- \end{itemize}
- \item Is there a relationship between defects  and libraries:
- \begin{itemize}
- \item Does defects in a librarie cause defect in other libraries?
- \item Does some libraries always have defects together?
- \end{itemize}
+ \item What is the nomber of defect per library?
  \item How long in average does it take to open and close a ticket?
@@
 For each problem, we experiement on the ticket database. 
- \subsubsection{Correlation between defects }
+ \subsubsection{Number of defects per librarie}
 We plot  defects and evolution per library over time.
 In x axis we have years and in y axis  we have the number of defects  or evolutions.
-According to  the visualizations, some libraries trends to as many defects as  evolution over time.
-For some libraries, we observe that they do not have defects.
-Some others seem to  have defects after evolution.
+This give us an overview of defect  history per library.
+And  which libraries   trend to have defects.
+
  \section{Results and Discussion}\label{sec:results-discussion}

### 2019-11-19 article.tex
updated the article

@@
 
-\title{Toward  maintainance of  a commencial software: Defects model  using moving average and regression}
+\title{Improving practices in a small french  company: first step}
 % \title{Toward  maintainance of  a commencial software: Time serie model of defects }
@@
 Legacy systems are known to be hard to maintain.
-This is the case in a french company whose main product is twenty years old software written in PowerBuilder (we call it SPB).
+This is the case in a french company whose main product is twenty years old software written in PowerBuilder.
 Our longterm goal is to help reengineer.
 But how to validate our intervention?
-Using moving average, and regression, we evaluate the maintenance state of SPB and produce a dashboard to monitor our future actions.
-We validate our results with the developer team.
-We  In this paper, we present a lightweight defects model to help planning commercial software maintenance
+Using moving average, and regression, we evaluate the maintenance state of the system and produce a dashboard to monitor our future actions.
+ In this paper, we present a lightweight defects model to help planning commercial software maintenance.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Lagacy system, Defect model .
+Legacy system, software qulity model .
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Software companies usually invest time and energy to improve the quality of the software they develop to respond to the rising market demands.
-Features are developed in a hurry sometimes.
-As results, they  allow less resources for software refactoring to remove source code defects.
-As the software grows,  it becomes hard to improve or maintain.
-Rewriting this software require time and a lot of resources.
-At this point, one of the solutions is to reverse-engineer them.
-This is the situation in a French company which main business product is SPB.
+%Software companies usually invest time and energy to improve the quality of the software they develop to respond to the rising market demands.
+Software companies, beacause of maket demand, develop features  in a hurry sometimes.
+As a result, they have little spare resources to allocate to software quality improvement and code defect removal.
+As the software grows,  it becomes harder and harder to maintain.
+%Rewriting this software require time and a lot of resources.
+At this point, one of the solutions is to re-engineer them. 
+This is the situation in CIM, a small French company, which main business product  is the studied system.
 
-With over 3,000,000 lines of codes, continually updated for more than 20 years,  SPB is not versioned and not unit tested.
-Defects  are registered in a database without correlation with which part of the system is responsible for the bug.
-Old versions of SPB are lost until 2012.
-The original developers of SPB are part of the developers' team.
-So the currents developers only know SPB partially.
-So we could not completely rely on developers view of the system.
-Besides, there is also a misunderstanding between developer team and the business team.
-As the business team doesn't know the state of SPB.
-Our purpose is:
+The long period of growth and evolution of the systems, as well as staff changes, leads to the emergence of problems such as dead code, duplicate code, lack of testing, and obsolete documentation. 
+The developers at the origin of the application are no longer present, so a large part of the knowledge (and this at different levels of granularity) is dispersed and diffuse. 
+In other words, to evaluate the state of the system, we cannot completely rely on their knowledge of the system.
+The only usable information about the system is  its' source code and a database in which defects and evolution are registered.
+ In this paper,  purpose is:
 \begin{itemize}
-\item How to provides a report on the state of SPB to the entire company?
+\item How to provides a report on the state of the system to the entire company?
 \item How to monitor our reverse-engineering task?
@@
  This paper is structured as follows: we start we related works in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present our defect model. 
-In the section 4 we present our results and validation.
-We  conclude in section 5
+ In the section 4 we present our results and validation. We  conclude in section 5
 
 \section{Related Work}\label{sec:related-work}
-
+Research about software defect model for the reliable prediction of post-release defects in software is an ongoing and yet unresolved research topic.
+It was already discussed in multiple  publications \cite{Catal09,Hall2012, Hoss2017}.
+Steffen Herbold \cite{Herb19} propose a cost model for software defect prediction
+These models aims to predict post-release defects but our model aims to fit  defects dataset  in order our reengineering on the studied system.   
 \section{Defect Model}\label{sec:defectModel}
 \subsection{Moving average}
-A moving average is a statistic technic usually used to smooth a time serie data.
-The principle is to calculate the average of a certain number according to one by one time series values to reflect the numerical trend.
+A moving average is a statistic technic usually used to smooth a time serie data. Let $ (t_1,y_1) , (t_2,y_2) , . . ., (t_n,y_n) $ a time serie  where
 \begin{equation*} SMA_{n}=\frac{1}{n}\sum\nolimits_{t=k-n+1}^{k}A_{t}\tag{1} \end{equation*}
-\subsection{Presentation of SPB}
-SPB is  a 3,000,000 PowerBuilder project, developed for more than 20 years.
-SPB is now maintained by a team of 15 developers.
-SPB includes 120 Powerbuilder libraries.
-SPB libraries  is be grouped by business module .
-Figure  \ref{fig:pbArchitecture} give an overview of SPB achitecture.
-\begin{figure*}[!ht]
-    \centering
-    {\includegraphics[width=0.9\linewidth]{images/pbArchitecture.jpg}}
-    \caption{Simplified SPB achitecture.
-Very simplified architecture of SPB}\label{fig:pbArchitecture}
- \end{figure*} 
+\subsection{Presentation of the studied system}
+In general, legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
+This is the case of the studied system  which has a life cycle of  more than 20 years. 
+It has 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
+The system is not versioned and old versions are lost until 2012.
+
+Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
+A Powerbuilder application components are grouped by libraries.  
+A Powerbuilder library contains differents type of Objects: Datawindow, User object, Global function,  menu, etc. 
+Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
+Its version 2017 supports version control systems and the support is not stable.
+
 \subsection{Ticket}
@@
 \section{Methodology}\label{sec:methodology}
-We collected data  from the company Tickets database .  Then we procced to data cleaning.
+We collected data  from the company Tickets database .  
+Then we procced to data cleaning.
 The data analytics process is guided by the following research rule:
@@
 
-  The  datas are consistent  from 2004 to 2019 .
-We  remove all tickets, non related  to SPB and reformat durations per ticket.
-By inteviewing developers, we categorize tickets into to sets: tickets related to defects and tickets related two evolutions.
+The  data are consistent  from 2004 to 2019 . 
+We  remove all tickets, not related  to SPB and reformat durations per ticket.
+By inteviewing developers, we categorize tickets into two sets: tickets related to defects and tickets related to evolutions.
 
- \subsection{Problems}
+ \subsection{Questions}
  \begin{itemize}
+ \item How to avoid the system souce code lost?
  \item What is the nomber of defect per library?
- \item How long in average does it take to open and close a ticket?
- \item How long in average  does a developer spend on a ticket ?
- \item How long in average does a developer spend to test a ticket after development ?
+ \item How long on average, does it take to open and close a ticket?
+ \item How long on average,  does a developer spend on a ticket ?
+ \item How long on average, does a developer spend to test a ticket after development ?
  \item Does the team manager estimate well  the time needed by the developer?
@@
 For each problem, we experiement on the ticket database. 
- \subsubsection{Number of defects per librarie}
-We plot  defects and evolution per library over time.
-In x axis we have years and in y axis  we have the number of defects  or evolutions.
-This give us an overview of defect  history per library.
-And  which libraries   trend to have defects.
+\subsubsection{Avoid the system souce code lost}
+The system source code is not versioned.  Some versions of the system are lost. 
+When developers work in the same version of the system, they chat with each other to notify which part of the system they are modifying so that others won't modify the same part to avoid losing modifications.
+Besides, each developer has to write in a comment in the source code his name and the date in the form of each modification he made.
+We believe that writing author in a comment in the source can be easily handled by a version control system.
+This is because of Powerbuilder support version controlling system from the 2017 release. 
+The support provided by Powerbuilder is not stable.
+The conflict resolution option is limited and a simple copy-paste of a library require a huge walkaround to update files. 
+With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion. 
+ \subsubsection{Number of defects per library}
+We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolutions.
+This give us an overview of defect  history per library. And  which libraries   trend to have defects.
+\subsubsection{ Average time to open and close a ticket}
+A ticket is closed when the task it is related to is done and validated. 
+We use the time a ticket remains open over the life cycle of the studied system as an indicator of the system state. 
+We grouped tickets by the month of creation.
+We then compute the average of  the duration between the time when the ticket is created and the time when the ticket is closed for each month.  
+We do this for tickets categorized as defect and tickets categorized as evolution. 
+We finally plot the result of each category into a graph.  First, the plot exhibits rapid up-and-down variation.
+We could not derive any trend from this variation. 
+We smooth the plot using the simple moving average of order 4 on the data.  
+We then plot the linear regression to fit the data.
 
+\subsubsection{Time developer spend on a ticket }
+When a developer work on the task assign to in a ticket, he spend time to analyse  the task.
+He then implement a solution and then test.
+The time spend analyzing and implementing the task assign in a ticket depend on the workload  of the ticket, the complexity of system, etc.
+We compute the average time spent by developers per month. 
+The data also present rapid up-and-down variation, which we smooth with simple moving average of order 4. We use  linear regression to fit the data.   
+\subsubsection{Average time  to test a ticket after development}
+Generally, when a developer finishes a development related to a ticket, he tests his solution.  
+The testing time is recorded in the ticket database.
+ We use this information to compute the average per month of testing time. 
+ \subsubsection{Team Manager time estimation}
+For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
+This estimation is based on the experience of the team manager.  
+We compare the time spent by the developer with the estimation per month over the life cycle of the system.  
+This is to assess if the developer has enough time to develop good quality source code.
+ We smooth data related to the comparisons and plot it to see the trend over the system life cycle.
  \section{Results and Discussion}\label{sec:results-discussion}

### 2019-11-19 article.tex
complete moving average definition

@@
 	\subsection{Moving average}
-A moving average is a statistic technic usually used to smooth a time serie data. Let $ (t_1,y_1) , (t_2,y_2) , . . ., (t_n,y_n) $ a time serie  where
-\begin{equation*} SMA_{n}=\frac{1}{n}\sum\nolimits_{t=k-n+1}^{k}A_{t}\tag{1} \end{equation*}
+	A moving average is a statistic technic usually used to smooth a time serie data and estimate it trend.
+The moving average of a period m is a series of consecutive averages of m terms at a time.
+The simple moving average is calculated as:
+
+	\begin{equation}
+	SMA_{t+1}=\frac{\sum\limits_{i=t-m}^t X_i}{m}
+	\end{equation}
 	\subsection{Presentation of the studied system}
@@
 	We could not derive any trend from this variation. 
-We smooth the plot using the simple moving average of order 4 on the data.  
+	We smooth the plot using the simple moving average of period 4 on the data.  
 	We then plot the linear regression to fit the data.
@@
 	We compute the average time spent by developers per month. 
-The data also present rapid up-and-down variation, which we smooth with simple moving average of order 4. We use  linear regression to fit the data.   
+	The data also present rapid up-and-down variation, which we smooth with simple moving average of period 4. We use  linear regression to fit the data.   
 	\subsubsection{Average time  to test a ticket after development}

### 2019-11-25 article.tex
update
I use overleaf. It doesn't allow the integration with git .

@@
 \usepackage{blindtext}
-
+\usepackage{float}
+\usepackage[font=scriptsize]{caption}
+\usepackage[sort&compress,square,comma,authoryear]{natbib}
 %\newcommand{\sd}[1]{\textbf{"\textsc{SD:}} \textit{#1}"}
@@
 
-	\title{Improving practices in a small french  company: first step}
+\title{Improving practices in a medium french  company: First step}
 % \title{Toward  maintainance of  a commencial software: Time serie model of defects }
@@
 \begin{abstract}
-	Legacy systems are old software that style does useful tasks.
-	In industrial software companies, legacy systems are often crucial for the company business model and represent a longterm business investment.
+Legacy systems are old software that still does useful tasks.
+In industrial software companies, legacy systems are often crucial for the company business model and represent a long-term business investment.
 Legacy systems are known to be hard to maintain.
 This is the case in a french company whose main product is twenty years old software written in PowerBuilder.
-	Our longterm goal is to help reengineer.
+Our long-term goal is to help re-engineer.
 But how to validate our intervention?
@@
 \begin{IEEEkeywords}
-	Legacy system, software qulity model .
+Legacy system, software quality model .
 \end{IEEEkeywords}
@@
 %Software companies usually invest time and energy to improve the quality of the software they develop to respond to the rising market demands.
-	Software companies, beacause of maket demand, develop features  in a hurry sometimes.
+Software companies, because of market demand, develop features  in a hurry .
 As a result, they have little spare resources to allocate to software quality improvement and code defect removal.
@@
 %Rewriting this software require time and a lot of resources.
-	At this point, one of the solutions is to re-engineer them. 
-	This is the situation in CIM, a small French company, which main business product  is the studied system.
+At this point, one of the solutions is to re-engineer it. 
+This is the situation at CIM, a medium French company, which main business product  is the studied system.
 
-	The long period of growth and evolution of the systems, as well as staff changes, leads to the emergence of problems such as dead code, duplicate code, lack of testing, and obsolete documentation. 
+The long period of growth and evolution of the systems, as well as staff changes, leads to the emergence of problems such as dead code, duplicate code, and obsolete documentation. 
 The developers at the origin of the application are no longer present, so a large part of the knowledge (and this at different levels of granularity) is dispersed and diffuse. 
-	In other words, to evaluate the state of the system, we cannot completely rely on their knowledge of the system.
-	The only usable information about the system is  its' source code and a database in which defects and evolution are registered.
-	 In this paper,  purpose is:
+In other words, we cannot completely rely on current developers knowledge of the system.
+The only usable information about the system is  its non versioned source code and a database in which defects and evolution are registered.
+ In this paper, we are trying to answer to the following questions:
 \begin{itemize}
@@
 \end{itemize}
-	We use defect model and analytics to overcome our problems.
-	 This paper is structured as follows: we start we related works in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present our defect model. 
+We use defect model and analytic to overcome our problems.
+ This paper is structured as follows: we start with related works in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present our defect model. 
  In the section 4 we present our results and validation. We  conclude in section 5
@@
 \section{Related Work}\label{sec:related-work}
-	Research about software defect model for the reliable prediction of post-release defects in software is an ongoing and yet unresolved research topic.
-It was already discussed in multiple  publications \cite{Catal09,Hall2012, Hoss2017}.
-	Steffen Herbold \cite{Herb19} propose a cost model for software defect prediction
-	These models aims to predict post-release defects but our model aims to fit  defects dataset  in order our reengineering on the studied system.   
+A software defect is a mistake at coding level, which manifests in a deviation from expected behavior .
+Mining a software defect history help to collect valuable information about the software life evolution.
+Software re-engineering monitoring should be supported by prediction models that predict the quality under control (\cite{Lenar17}). 
+In the literature, software defect history combined with static source code metrics and or developers metric to monitor maintenance quality.
+
+Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
+This approach was already discussed in multiple  publications \cite{Catal09, Hall12, Hoss17, Li19a, malh15,bibi06, Tanti16}.
+
+\cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
+Dan Port and Bill Taber \cite{port18} use the number of  bugs difference between release, reported bugs per logical lines of code, number of day between releases, the system size change between release, the size change per day, the time spent  per bugs, test per logical line of code, comment per logical line of code to evaluate software development policy  to monitor maintenance quality of a software at Jet propulsion Laboratory.
+
 \section{Defect Model}\label{sec:defectModel}
 \subsection{Moving average}
-	A moving average is a statistic technic usually used to smooth a time serie data and estimate it trend.
+A moving average is a statistic technical usually used to smooth a time series data and estimate it trend \cite{MOLU17}.
  The moving average of a period m is a series of consecutive averages of m terms at a time. 
@@
 \subsection{Presentation of the studied system}
-	In general, legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
-	This is the case of the studied system  which has a life cycle of  more than 20 years. 
-	It has 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
+Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
+This is the case of the studied system  which has more than 20 years. 
+It's a 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
 The system is not versioned and old versions are lost until 2012.
@@
 Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
-	A Powerbuilder application components are grouped by libraries.  
+Powerbuilder applications components are grouped by libraries.  
 A Powerbuilder library contains differents type of Objects: Datawindow, User object, Global function,  menu, etc. 
 Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
-	Its version 2017 supports version control systems and the support is not stable.
+Its version 2017 supports version control systems.% and the support is not stable.
 
@@
 \end{itemize}
-
+In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.
 \section{Methodology}\label{sec:methodology}
 We collected data  from the company Tickets database .  
-	Then we procced to data cleaning.
-	The data analytics process is guided by the following research rule:
+Then we proceed to data cleaning.
+The data analytic process is guided by the following research methodology:
 \begin{itemize}
 \item Pose a problem
-	\item Make experimentations on data
+\item Make experimentation on data
 \item Validation of results
@@
 The ticket database contains data from 1998  until 2019. 
-	This data includes tickets  differents teams and softwares in  the company. 
+This data includes tickets  different teams and software in  the company. 
 In the field related to the  library a ticket is related to,  the name of the library is not always well written.
 
-	The  data are consistent  from 2004 to 2019 . 
-	We  remove all tickets, not related  to SPB and reformat durations per ticket.
-	By inteviewing developers, we categorize tickets into two sets: tickets related to defects and tickets related to evolutions.
+We use tickets database data from 2004 to 2019 . 
+We  remove all tickets, not related  to the studied system and reformat duration per ticket.
+By interviewing developers, we categorize tickets into two sets: tickets related to defects and tickets related to evolution.
 
@@
  \begin{itemize}
-	 \item How to avoid the system souce code lost?
-	 \item What is the nomber of defect per library?
+ \item How to avoid the system source code lost?
+ \item What is the number of defect per library?
  \item How long on average, does it take to open and close a ticket?
@@
 
-	 \subsection{Experimentations}
-	For each problem, we experiement on the ticket database. 
-	\subsubsection{Avoid the system souce code lost}
+ \subsection{Experimentation}
+
+\subsubsection{Avoid the system source code lost}
 The system source code is not versioned.  Some versions of the system are lost. 
@@
 The support provided by Powerbuilder is not stable.
-	The conflict resolution option is limited and a simple copy-paste of a library require a huge walkaround to update files. 
+The conflict resolution option is limited and a simple copy-paste of a library require a huge walk-around to update files. 
 With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion. 
  \subsubsection{Number of defects per library}
-	We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolutions.
+We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolution.
 This give us an overview of defect  history per library. And  which libraries   trend to have defects.
@@
 We then plot the linear regression to fit the data.  
+The figure \ref{fig:evol} presents the trend of time to close evolution ticket and  the figure \ref{fig:defect} shows  the trends  of time to close defects tickets.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=50mm]{./images/openCloseEvol.png}
+  \caption{Time to close evolution tickets}
+  \label{fig:evol}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=50mm]{./images/openCloseBug.png}
+  \caption{Time to close defects tickets}
+  \label{fig:defect}
+\end{figure}
 
@@
 The data also present rapid up-and-down variation, which we smooth with simple moving average of period 4. We use  linear regression to fit the data.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=70mm]{./images/devDefect.png}
+  \caption{Time spent by a developer to implement solution for  defects tickets}
+  \label{fig:devTimeDefect}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=70mm]{./images/devEvol.png}
+  \caption{Time spent by a developer to implement solution for  evolution tickets}
+  \label{fig:devTimeEvol}
+\end{figure}
 \subsubsection{Average time  to test a ticket after development}
@@
  We use this information to compute the average per month of testing time. 
+ \begin{figure}[H]
+  \centering
+  \includegraphics[width=50mm]{./images/timeDevTest.png}
+  \caption{Time spent by a developer to test his solution for  defect tickets}
+  \label{fig:devTimeTestBug}
+\end{figure}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=50mm]{./images/evolutionTest.png}
+  \caption{Time spent by a developer to test his solution for  evolution tickets}
+  \label{fig:devTimeTestEvol}
+\end{figure}
  \subsubsection{Team Manager time estimation}
@@
 This is to assess if the developer has enough time to develop good quality source code.
-	 We smooth data related to the comparisons and plot it to see the trend over the system life cycle.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=70mm]{./images/estimateBug.png}
+  \caption{Actual time spent by the developer minus time estimated by the manager for defect tickets.
+The yAxis represent the value of the gap between the development time and the estimated time in hour.
+The xAxis represent months from 2004 to 2019}
+  \label{fig:devEstDefect}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=70mm]{./images/estimateEvol.png}
+  \caption{Actual time spent by the developer minus time estimated by the manager for evolution tickets. 
+    The yAxis represent the value of the gap between the development time and the estimated time in hour. 
+    The xAxis represent months from 2004 to 2019}
+  \label{fig:devEstEvol}
+\end{figure}
 \section{Results and Discussion}\label{sec:results-discussion}
+\begin{itemize}
+    \item Developers are now using subversion to integrate all their changes in the system. 
+    \item From 2004 to 2019, as we can see in figure \ref{fig:evol} and figure \ref{fig:defect} ,  the time to close a ticket is 5 times the time at 2004 for defects and 1.5 times for evolution.
+    \item Developers spend 4 times the time spent at 2004 for evolution tickets figure \ref{fig:devTimeEvol}, and  3 times for defects tickets figure \ref{fig:devTimeDefect}.
+    \item  Figure \ref{fig:devTimeTestEvol} and \ref{fig:devTimeTestBug} show that the developer spend in average 45 minutes test  the feature implemented of the fixed defect.
+    \item The time estimated by the developers team manager trend to be enough for the developer from 2013 for defects tickets and evolutions tickets.
+\end{itemize}
 
 \section{Summary and Conclusions}\label{sec:conclusion}
-
-	%\bibliographystyle{IEEEtran}
-	\bibliographystyle{alpha}
-	\bibliography{rmod,others,new}
+In this paper we present our first step in  improving practices in a french company. We first introduce subversion, a version control system.
+The developers team is now using it and the software studied source code is now versioned.
+This open the door for further analysis of the code repository to understand the system evolution. 
+Using the ticket database, the moving average and regression line, we build a defect model mainly assess the developer effort throughout the project life cycle.
+We will use this model to monitor our future actions which is: how to decompose the system big methods.
+\bibliographystyle{plainnat}
+%\bibliographystyle{alpha}
+\bibliography{rmod,new}
 

### 2019-11-25 article.tex
remove a citation
add a comment
review with Nicolas

@@
 This is the case in a french company whose main product is twenty years old software written in PowerBuilder.
-Our long-term goal is to help re-engineer.
+Our long-term goal is to help it re-engineer this system.
 But how to validate our intervention?
-Using moving average, and regression, we evaluate the maintenance state of the system and produce a dashboard to monitor our future actions.
- In this paper, we present a lightweight defects model to help planning commercial software maintenance.
+Little data is available on the system and specifically, past versions of the source code are not easy to recover.
+This constrained us on the metrics we could use.
+%We evaluate the maintenance state of the system and produce a dashboard to monitor our future actions.
+In this paper, we present a lightweight model to characterize the situation of the system and allow us to monitor it in the future.
 \end{abstract}
@@
 \section{Introduction}
+%-------------------------------------------------------------------------------
+
 %Software companies usually invest time and energy to improve the quality of the software they develop to respond to the rising market demands.
-Software companies, because of market demand, develop features  in a hurry .
-As a result, they have little spare resources to allocate to software quality improvement and code defect removal.
-As the software grows,  it becomes harder and harder to maintain.
+Software companies have little spare resources to allocate to software quality improvement or code defect removal.
+As a result they often develop features in a hurry.
+As the system grows, it becomes harder and harder to maintain.
 %Rewriting this software require time and a lot of resources.
-At this point, one of the solutions is to re-engineer it. 
-This is the situation at CIM, a medium French company, which main business product  is the studied system.
+To ensure the future of the system, and through it, of the company itself, some re-engineering actions might be necessary.
+Long period of growth and evolution of the systems as well as staff evolution, lead to problems such as dead code, duplicate code, and obsolete documentation. 
+The developers at the origin of the application are no longer present, so a large part of the knowledge (and this at different levels of granularity) is scattered or lost.
 
-The long period of growth and evolution of the systems, as well as staff changes, leads to the emergence of problems such as dead code, duplicate code, and obsolete documentation. 
-The developers at the origin of the application are no longer present, so a large part of the knowledge (and this at different levels of granularity) is dispersed and diffuse. 
-In other words, we cannot completely rely on current developers knowledge of the system.
-The only usable information about the system is  its non versioned source code and a database in which defects and evolution are registered.
- In this paper, we are trying to answer to the following questions:
-\begin{itemize}
-\item How to provides a report on the state of the system to the entire company?
-\item How to monitor our reverse-engineering task?
-\end{itemize}
-We use defect model and analytic to overcome our problems.
- This paper is structured as follows: we start with related works in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present our defect model. 
- In the section 4 we present our results and validation. We  conclude in section 5
+This is the situation at CIM, a medium French company, which main business product we are studying.
+The system is written in an old language (PowerBuilder) typically unknown to young programmers which translates in a difficulty to hire new developpers.
+There is also a sense in the development team that the system suffers from architecture erosion and is difficult to maintain or evolve which translates into a steep learning curve for new developpers.
+We are trying to help this company improve its software engineering practices and restructure the system to improve the situation.
 
-\section{Related Work}\label{sec:related-work}
-A software defect is a mistake at coding level, which manifests in a deviation from expected behavior .
-Mining a software defect history help to collect valuable information about the software life evolution.
+In this paper, we are trying to answer the following question:
+How to validate our intervention and can we measure its concrete impact on the system and its evolution?
+
+%How to provides a report on the state of the system to the entire company?
+For the reasons explained above, we cannot completely rely on current developers knowledge of the system.
+The only usable information about the system is its non versioned source code and a ticket database.
+Past literature often relied on historical data on the source code, for example
+cyclomatic complexity \cite{gill91}, or number of lines of code \cite{port18}.
+In lack of a reliable software versonning system, we could not use these solutions.
+
+We mine and analyse the ticket database to overcome our problem.
+This paper presents the results of this work.
+
+ This paper is structured as follows: we start with related work in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present ticket database mining background.
+ In the section 4 we present our results and validation. We  conclude in section 5.
+
+\section{Related Work}
+%-------------------------------------------------------------------------------
+\label{sec:related-work}
+
+"intro": de quoi on va parler et pourquoi en parler ?
+
+%A software defect is a mistake at coding level, which manifests in a deviation from expected behavior. 
+%Mining a software defect history helps to collect valuable information about the software life evolution. 
 Software re-engineering monitoring should be supported by prediction models that predict the quality under control (\cite{Lenar17}).
-In the literature, software defect history combined with static source code metrics and or developers metric to monitor maintenance quality.
 
-Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
-This approach was already discussed in multiple  publications \cite{Catal09, Hall12, Hoss17, Li19a, malh15,bibi06, Tanti16}.
+%Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
 
-\cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
+Software defect prediction has already been extensively discussed in literature in numerous publications.
+This literature is summarised in many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
+
+Software defect history combined with static source code metrics and or developers metric to monitor maintenance quality.
+For example \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
 Dan Port and Bill Taber \cite{port18} use the number of  bugs difference between release, reported bugs per logical lines of code, number of day between releases, the system size change between release, the size change per day, the time spent  per bugs, test per logical line of code, comment per logical line of code to evaluate software development policy  to monitor maintenance quality of a software at Jet propulsion Laboratory.
 
-\section{Defect Model}\label{sec:defectModel}
+"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
+donc: on develop notre propre analyse sur la ticket db.
+
+\section{Defect Model}
+%-------------------------------------------------------------------------------
+\label{sec:defectModel}
+
 \subsection{Moving average}
+%-------------------------------------------------------------------------------
+
 A moving average is a statistic technical usually used to smooth a time series data and estimate it trend \cite{MOLU17}.
@@
 \end{equation}
+
 \subsection{Presentation of the studied system}
+%-------------------------------------------------------------------------------
 Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
@@
 \subsection{Ticket}
+%-------------------------------------------------------------------------------
+
 A ticket is related do a task to do. 
@@
 A ticket has the following characteristics:
+
 \begin{itemize}
@@
 In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.
-\section{Methodology}\label{sec:methodology}
+
+\section{Methodology}
+%-------------------------------------------------------------------------------
+\label{sec:methodology}
+
 We collected data  from the company Tickets database .  
@@
 \end{itemize}
+
 \subsection{Data collection and data cleaning}
+%-------------------------------------------------------------------------------
+
 The ticket database contains data from 1998  until 2019. 
@@
 \subsubsection{Avoid the system source code lost}
+%-------------------------------------------------------------------------------
+
 The system source code is not versioned.  Some versions of the system are lost. 
@@
 With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion.
+
  \subsubsection{Number of defects per library}
+ %-------------------------------------------------------------------------------
+
 We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolution.
 This give us an overview of defect  history per library. And  which libraries   trend to have defects.
+
 \subsubsection{ Average time to open and close a ticket}
+%-------------------------------------------------------------------------------
+
 A ticket is closed when the task it is related to is done and validated. 
@@
 The figure \ref{fig:evol} presents the trend of time to close evolution ticket and  the figure \ref{fig:defect} shows  the trends  of time to close defects tickets.
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=50mm]{./images/openCloseEvol.png}
+  \includegraphics[width=70mm]{./images/openCloseEvol.png}
   \caption{Time to close evolution tickets}
@@
   \centering
-  \includegraphics[width=50mm]{./images/openCloseBug.png}
+  \includegraphics[width=70mm]{./images/openCloseBug.png}
   \caption{Time to close defects tickets}
@@
 \subsubsection{Time developer spend on a ticket }
+%-------------------------------------------------------------------------------
+
 When a developer work on the task assign to in a ticket, he spend time to analyse  the task. 
@@
 \end{figure}
+
 \subsubsection{Average time  to test a ticket after development}
+%-------------------------------------------------------------------------------
+
 Generally, when a developer finishes a development related to a ticket, he tests his solution.  
@@
  We use this information to compute the average per month of testing time.
+
  \begin{figure}[H]
   \centering
-  \includegraphics[width=50mm]{./images/timeDevTest.png}
+  \includegraphics[width=70mm]{./images/timeDevTest.png}
   \caption{Time spent by a developer to test his solution for  defect tickets}
@@
 \end{figure}
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=50mm]{./images/evolutionTest.png}
+  \includegraphics[width=70mm]{./images/evolutionTest.png}
   \caption{Time spent by a developer to test his solution for  evolution tickets}
@@
 \end{figure}
+
  \subsubsection{Team Manager time estimation}
+ %-------------------------------------------------------------------------------
+
 For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
@@
 This is to assess if the developer has enough time to develop good quality source code.
+
 \begin{figure}[H]
@@
 \end{figure}
-\section{Results and Discussion}\label{sec:results-discussion}
+
+\section{Results and Discussion}
+%-------------------------------------------------------------------------------
+\label{sec:results-discussion}
+
 \begin{itemize}
@@
 
-\section{Summary and Conclusions}\label{sec:conclusion}
+\section{Summary and Conclusions}
+%-------------------------------------------------------------------------------
+\label{sec:conclusion}
+
 In this paper we present our first step in  improving practices in a french company. We first introduce subversion, a version control system.

### 2019-11-25 article.tex
update the related work section

@@
 \label{sec:related-work}
-
-"intro": de quoi on va parler et pourquoi en parler ?
+Recently, research on mining software repositories has received much attention as it has attempted to  understand  software  evolution \cite{Zhan10a}.
+Software defect history and source code history are often used to monitor software maintenance or predict the number of defect in a system.
+For instance, software defect prediction using software repositories, has already been extensively discussed in literature in numerous publications.
+This literature is summarised in many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
+%"intro": de quoi on va parler et pourquoi en parler ?
 
@@
 %Mining a software defect history helps to collect valuable information about the software life evolution. 
-Software re-engineering monitoring should be supported by prediction models that predict the quality under control (\cite{Lenar17}).
+%Software re-engineering monitoring should be supported by prediction models that predict the quality under control (\cite{Lenar17}).
 
 %Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
+ \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
+Dan Port and Bill Taber \cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution for maintenance monitoring.
 
-Software defect prediction has already been extensively discussed in literature in numerous publications.
-This literature is summarised in many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
-
-Software defect history combined with static source code metrics and or developers metric to monitor maintenance quality.
-For example \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
-Dan Port and Bill Taber \cite{port18} use the number of  bugs difference between release, reported bugs per logical lines of code, number of day between releases, the system size change between release, the size change per day, the time spent  per bugs, test per logical line of code, comment per logical line of code to evaluate software development policy  to monitor maintenance quality of a software at Jet propulsion Laboratory.
-
-"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
-donc: on develop notre propre analyse sur la ticket db.
+In this paper, we are interested to evaluate the system to monitor the re-engineering of the system.
+But we do not have the source code historical data.
+Thus, we cannot use the methods presented in above-mentionned literature.
+We develop a lightweight technique to analyse the ticket database .
+%"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
+%donc: on develop notre propre analyse sur la ticket db.
 

### 2019-11-26 __latexindent_temp.tex
Nicolas correction

--- 2019-11-25 article.tex
@@
 \label{sec:related-work}
-Recently, research on mining software repositories has received much attention as it has attempted to  understand  software  evolution \cite{Zhan10a}.
-Software defect history and source code history are often used to monitor software maintenance or predict the number of defect in a system.
-For instance, software defect prediction using software repositories, has already been extensively discussed in literature in numerous publications.
-This literature is summarised in many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
+Recently, research on mining software repositories has received much attention as it attempts to  understand  software  evolution \cite{Zhan10a}.
+Software defect history and source code history are often used to monitor software maintenance or predict the system's quality. 
+For instance, software defect prediction using software repositories, has already been extensively discussed in literature as witnessed by many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
 %"intro": de quoi on va parler et pourquoi en parler ?
@@
 %Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
- \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
-Dan Port and Bill Taber \cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution for maintenance monitoring.
+But these solutions rely on the availability of source code history. 
+For example, \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
+\cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution to monitor maintenance.
 
-In this paper, we are interested to evaluate the system to monitor the re-engineering of the system.
-But we do not have the source code historical data.
-Thus, we cannot use the methods presented in above-mentionned literature.
-We develop a lightweight technique to analyse the ticket database .
+In our case, the source code history is not easily available as the company does not make use of a version control system.
+Thus, we cannot use the methods presented above.
+
+Other researchers considered ticket database to characterize a system.
+
+We develop a lightweight technique to analyse the ticket database.
+
 %"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
@@
 
-\section{Defect Model}
+\section{Study background}
 %-------------------------------------------------------------------------------
 \label{sec:defectModel}
+
+In this paper, we are interested in characterising the system and its evolution to better evaluate the possible future impact of our intervention.
+
+\subsection{Presentation of the studied system}
+%-------------------------------------------------------------------------------
+
+Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
+This is the case of the system we are studying which is older than 20 years. 
+It's a 3 MLOC software written in Powerbuilder.
+
+Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
+Powerbuilder application components are grouped in libraries.  
+A Powerbuilder library contains differents type of objects: datawindow, user object, global function,  menu, etc. 
+Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
+Its 2017 version  supports version control but for historical reasons it was never used on the system studied.% and the support is not stable.
+
+With 117 Powerbuilder libraries, the  bigest library is  over 300 KLOC.
+The system is not versioned in a version control system but some old major versions or archivied in separate directories.
+Old versions (before 2012) are completely lost.
+
+\subsection{Ticket}
+%-------------------------------------------------------------------------------
+
+A ticket is related do a task to do and it is used for billing. 
+This task can be fixing a defect, writing documentation, adding a new feature, etc. 
+Once the task is done and validated, the ticket is close.
+At CIM, a ticket has the following characteristics:
+
+\begin{itemize}
+\item the creation date
+\item the closing date
+\item the library(ies) it is related to
+\item time spent by a developer
+  \begin{itemize}
+\item time to analyze
+\item time to implement solution
+\item time to test
+  \end{itemize}
+\item  the estimation of the time needed by the developer to work on the ticket
+\end{itemize}
+In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.
 
@@
 \end{equation}
-
-\subsection{Presentation of the studied system}
-%-------------------------------------------------------------------------------
-Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
-This is the case of the studied system  which has more than 20 years. 
-It's a 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
-The system is not versioned and old versions are lost until 2012.
-
-Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
-Powerbuilder applications components are grouped by libraries.  
-A Powerbuilder library contains differents type of Objects: Datawindow, User object, Global function,  menu, etc. 
-Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
-Its version 2017 supports version control systems.% and the support is not stable.
-
-\subsection{Ticket}
-%-------------------------------------------------------------------------------
-
-A ticket is related do a task to do. 
-This task can be fixing a defect, writing documentation, adding a new feature, etc. 
-A ticket is open for a task . 
-Once the task is done and validated, the ticket is close.
-A ticket has the following characteristics:
-
-\begin{itemize}
-\item the libraries it  is related to
-\item the creation date
-\item the closing date
-\item time spent by a developer
-  \begin{itemize}
-\item time to analyze
-\item time to implement solution
-\item time to test
-  \end{itemize}
-\item  the estimation of the time needed by the developer to work on the ticket
-\end{itemize}
-In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.
 

### 2019-11-27 article.tex
add comment to figure

@@
 
- This paper is structured as follows: we start with related work in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present ticket database mining background.
- In the section 4 we present our results and validation. We  conclude in section 5.
+ This paper is structured as follows: we start with related work in the section \ref{sec:related-work}, followed by  the section \ref{sec:background}  in which we present ticket database mining background.
+ In the section \ref{sec:methodology} we present our methodology. In section \ref{sec:results-discussion} we discussed our results and   conclude in section \ref{sec:conclusion}.
 
@@
 %Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
- \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
-Dan Port and Bill Taber \cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution for maintenance monitoring.
+But these solutions rely on the availability of source code history. 
+For example, \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
+\cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution to monitor maintenance.
 
-In this paper, we are interested to evaluate the system to monitor the re-engineering of the system.
-But we do not have the source code historical data.
-Thus, we cannot use the methods presented in above-mentionned literature.
-We develop a lightweight technique to analyse the ticket database .
+In our case, the source code history is not easily available as the company does not make use of a version control system.
+Thus, we cannot use the methods presented above.
+
+\cite{Herz13a} propose to consider ticket database.
+He reports that $33.8\%$ of the bugs studied among five open source projects were misclassified.
+For this reason, other researchers try to automatically re-classify maintenance activities (e.g. \cite{Mock20a,Levin19a}).
+
+%Other researchers considered ticket database to characterize a system. For instance, \cite{Levin19a} 
+At CIM, maintenance activities classification is more reliable because it drives the entire software evolution process.
+We rely on this classification to make our analysis.
+
+We develop a lightweight technique to analyse the ticket database.
+
 %"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
@@
 
-\section{Defect Model}
+\section{Study background}
 %-------------------------------------------------------------------------------
-\label{sec:defectModel}
+\label{sec:background}
 
-\subsection{Moving average}
+In this paper, we are interested in characterising the system and its evolution to better evaluate the possible future impact of our intervention.
+
+\subsection{Presentation of the system studied}
 %-------------------------------------------------------------------------------
 
-A moving average is a statistic technical usually used to smooth a time series data and estimate it trend \cite{MOLU17}.
- The moving average of a period m is a series of consecutive averages of m terms at a time. 
- The simple moving average is calculated as:
+Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
+This is the case of the system we are studying which is more than 20 years old. 
+It is written in Powerbuilder.
+Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
+Powerbuilder application components are grouped in libraries.  
+A Powerbuilder library contains differents type of objects: datawindow, user object, global function,  menu, etc. 
+Powerbuilder is a procedural language that evolved to (partial) object-orientedness: inheritance and object-oriented features are limited to some object types (windows, user objects and menus).
 
-\begin{equation}
-SMA_{t+1}=\frac{\sum\limits_{i=t-m}^t X_i}{m}
-\end{equation}
+The system has 3 MLOC, in 117 Powerbuilder libraries.
+The  largest library is  over 300 KLOC.
+The development team varied over time but counts 15 people at the moment, without the testing team which is external to developpement.
 
-\subsection{Presentation of the studied system}
-%-------------------------------------------------------------------------------
-Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
-This is the case of the studied system  which has more than 20 years. 
-It's a 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
-The system is not versioned and old versions are lost until 2012.
-
-Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
-Powerbuilder applications components are grouped by libraries.  
-A Powerbuilder library contains differents type of Objects: Datawindow, User object, Global function,  menu, etc. 
-Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
-Its version 2017 supports version control systems.% and the support is not stable.
+PowerBuilder version supports version control only since its 2017 version, and even this supports is still not entirelly satisfying, for example
+conflict resolution is performed automatically by the system by choosing one version over the other without asking the developer.
+For these reasons, version control management was never used on the system studied.% and the support is not stable. 
+However some old major versions or archived in separate directories.
+Versions before 2012 are completely lost.
+Some version control is done informally inside the team.
+When developers work on the same version of the system, they chat with each other to notify which part they are modifying so that others won't modify the same part.
+Also, each developer has to write a comment in the source code with his/her name and the date the modification he/she performed. 
+%We believe that writing author in a comment in the source can be easily handled by a version control system.
 
@@
 %-------------------------------------------------------------------------------
+% depuis quand ?
+% tres important car utilise dans toute la boite: affectatin du travail, workflow, facturation
 
-A ticket is related do a task to do. 
-This task can be fixing a defect, writing documentation, adding a new feature, etc. 
-A ticket is open for a task . 
-Once the task is done and validated, the ticket is close.
-A ticket has the following characteristics:
+At CIM, tickets are stored in the tickets database since 2000.
+A ticket represent a unit work.
+The ticket database drives the entire software evolution process: assignement of work to developers, management of the workflow to answer a client request, billing information about each task.
+There are tickets for fixing defects, writing documentation, adding new feature, etc. 
+As a consequence we can rely on a ticket's classification because it is reviewed by the team manager to ensure that it is properly handled.
+
+At CIM, a ticket includes the following characteristics among other things:
 
 \begin{itemize}
-\item the libraries it  is related to
 \item the creation date
 \item the closing date
+\item the estimation of the time needed by the developer to work on the ticket
 \item time spent by a developer
@@
   \end{itemize}
-\item  the estimation of the time needed by the developer to work on the ticket
+  \item the library(ies) impacted
 \end{itemize}
-In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.
 
@@
 
-We collected data  from the company Tickets database .  
-Then we proceed to data cleaning.
-The data analytic process is guided by the following research methodology:
+Our long-term goal is to help developers re-engineer the system at a small cost.
+This is need to improve the general quality and make future evolution easier, but it need to be cheap to convince upper management investing in this purely technical task.
+
+Therefore, we need to validate our intervention as well as the restructuring work developpers might engage into in the future.
+
+\subsection{Souce code versionning}
+%-------------------------------------------------------------------------------
+
+Our first action was to introduce a version management system.
+We chose  Subversion (SVN) because it was simpler to explain to developpers that were not familiar with the concepts of version management.
+We gave a short formation to the developpers and they are now starting to use it as part of the new process.
+
+In addition we are recontructing a summarized source history in SVN by importing one after the other the different major versions curently stored in directories (versions 2012 to 2019). 
+We hope that this will help us analyse the system historical code changes in order to have additionnal information about th system evolution.
+
+\subsection{Ticket data analysis}
+%-------------------------------------------------------------------------------
+
+Our goal was to characterize the system to be able to measure our impact and that of the developpers in the future.
+The problem was to extract information from the system that was relevant for the company and for which we could hope to have some impact.
+All this within the very restricted context described above.
+
+We turned to the ticket database and elected the following questions:
 \begin{itemize}
-\item Pose a problem
-\item Make experimentation on data
-\item Validation of results
+ \item What is the proportion of evolution versus correction tickets?
+ \item How long does it take to close a ticket?
+ \item Developement time spent on a ticket?
+ \item Testing time spent by the developer on a ticket?
+ \item Testing time spent by the tester (other team) on a ticket?
+ \item Difference between the time estimated and the actual time for a ticket?
  \end{itemize}
 
-\subsection{Data collection and data cleaning}
+%a revoir
+
+The ticket database first needed some cleaning:
+\begin{itemize}
+  \item Tickets may concern several software systems in the company and different development teams.
+  We thus selected tickets related to the system we are studing.
+
+  \item The ticket database contains data from 1998  until today. 
+  Before 2004, tickets information is not always consistent, for example, missing creation date or missing/incorrect category.
+  This constrained us to eliminate tickets prior to 2004.
+
+  \item Up to recently, the name of the library concerned by a ticket was filled manually (free text).
+  As a consequence, there are some typos in the names that need to be corrected.
+  A simple and frequent case is two swapped characters \emph{cwm\_liq\_ou} instead of \emph{cwm\_liq\_uo} (``uo'' PowerBuilder User Object).
+  Some more complex cases require an understanding of the application domain and the system, for example \emph{uo\_liq} instead of \emph{cwm\_liq\_uo}.
+  We identified all the errors manually and corrected them.
+
+  \item The category of the ticket is fine grained whereas we are only interest in evolution versus corrective tickets.
+  In our analysis we recategorize the tickets according to some simple dictionnary provided by the team manager.
+
+\end{itemize}
+
+For all the time questions, the tickets are grouped by month of creation and their value (for example time to close the ticket) are averaged for the month of creation. 
+We compute the data for our questions as follows:
+\begin{itemize}
+  \item We compute the \emph{closing time} of a ticket simply as the time between creation and closing of each (closed) ticket.
+\item %autre metric
+\end{itemize}
+
+We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (non stationary results) than made it diffcult to interpret the graphs.
+To get smoother plots, we finally computed the moving average of [month-2 ; month+2] for each month.
+Therefore, ploted data for july 2010 of any time metric correspond to average time of all tickets opened between may 2010 (inclusive) and september 2010 (inclusive).
+
+Finally to get a better notion of the trend, we will also plot the linear regression of the curve for each graph.
+
+\subsection{Results}
 %-------------------------------------------------------------------------------
 
-The ticket database contains data from 1998  until 2019. 
-This data includes tickets  different teams and software in  the company. 
-In the field related to the  library a ticket is related to,  the name of the library is not always well written.
-
-We use tickets database data from 2004 to 2019 . 
-We  remove all tickets, not related  to the studied system and reformat duration per ticket.
-By interviewing developers, we categorize tickets into two sets: tickets related to defects and tickets related to evolution.
-
- \subsection{Questions}
- \begin{itemize}
- \item How to avoid the system source code lost?
- \item What is the number of defect per library?
- \item How long on average, does it take to open and close a ticket?
- \item How long on average,  does a developer spend on a ticket ?
- \item How long on average, does a developer spend to test a ticket after development ?
- \item Does the team manager estimate well  the time needed by the developer?
- \item If the time estimated by the team manager is good, does the developer finish because  of time constraint?
- \end{itemize}
-
- \subsection{Experimentation}
-
-\subsubsection{Avoid the system source code lost}
+\subsection{Souce code versionning}
 %-------------------------------------------------------------------------------
 
-The system source code is not versioned.  Some versions of the system are lost. 
-When developers work in the same version of the system, they chat with each other to notify which part of the system they are modifying so that others won't modify the same part to avoid losing modifications.
-Besides, each developer has to write in a comment in the source code his name and the date in the form of each modification he made.
-We believe that writing author in a comment in the source can be easily handled by a version control system.
-This is because of Powerbuilder support version controlling system from the 2017 release. 
-The support provided by Powerbuilder is not stable.
-The conflict resolution option is limited and a simple copy-paste of a library require a huge walk-around to update files. 
-With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion.
+The introduction of SVN only started one month ago and we do not have yet significant results to report here.
 
- \subsubsection{Number of defects per library}
+For the reconstruction of the summarized source history, we already imported major versions until 2015 in a separated repository. 
+ %We then grouped them by major release. 
+ %We create an SVN repository in which we create a branch for each major release. We are pushing each release in the branch  of the major release it belong to.
+
+\subsubsection{Data collection}
 %-------------------------------------------------------------------------------
 
-We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolution.
-This give us an overview of defect  history per library. And  which libraries   trend to have defects.
+\begin{table}[htbp]
+  \begin{center}
+    \caption{Ticket analysed}
+    \label{tab:proportion}
+    \begin{tabular}{| l | c |c|}
+      \hline
+      Tickets & Defect  & Evolution  \\
+      \hline
+      27380&15407 ($56\%$)&11973 (44\%)\\
+      \hline 
+    \end{tabular}
+  \end{center}  
+\end{table}
 
-\subsubsection{ Average time to open and close a ticket}
+Table \ref{tab:proportion} gives the number of defect versus evolution tickets.
+We note that 56\% of defect tickets seems a high proportion.
+Literature (e.g. \cite{Pigo96a}) states that the proportion is typically 20\% to 25\% of defect tickets.
+This is an issue that we will investigate and monitor in the future.
+
+\subsubsection{Time to close a ticket}
 %-------------------------------------------------------------------------------
 
-A ticket is closed when the task it is related to is done and validated. 
-We use the time a ticket remains open over the life cycle of the studied system as an indicator of the system state. 
-We grouped tickets by the month of creation.
-We then compute the average of  the duration between the time when the ticket is created and the time when the ticket is closed for each month.  
-We do this for tickets categorized as defect and tickets categorized as evolution. 
-We finally plot the result of each category into a graph.  First, the plot exhibits rapid up-and-down variation.
-We could not derive any trend from this variation. 
-We smooth the plot using the simple moving average of period 4 on the data.  
-We then plot the linear regression to fit the data.  
-The figure \ref{fig:evol} presents the trend of time to close evolution ticket and  the figure \ref{fig:defect} shows  the trends  of time to close defects tickets.
-
-\begin{figure}[H]
+\begin{figure}[htbp]
   \centering
-  \includegraphics[width=70mm]{./images/openCloseEvol.png}
-  \caption{Time to close evolution tickets}
-  \label{fig:evol}
+  \includegraphics[width=70mm]{./images/openCloseEvol.png} \\
+  \includegraphics[width=70mm]{./images/openCloseBug.png}
+  \caption{Time to close evolution (up) and defect (down) tickets}
+  \label{fig:closingTime}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/openCloseBug.png}
-  \caption{Time to close defects tickets}
-  \label{fig:defect}
-\end{figure}
+Figure \ref{fig:closingTime} presents the trend of closing time for evolution (up) and defect (down) tickets.
+One can notice a large variation of ploted closing time, even after smoothing it with the moving average.
+It does not seem to be a problem.
 
-\subsubsection{Time developer spend on a ticket }
+It takes longer (on average) to close an evolution ticket than a defect ticket which seems natural.
+
+We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
+Finally we note that the closing time over the 15 years was multiplied by 2 for evolution tickets and 3 for defect tickets.
+Again this is an issue to investigate.
+
+\subsubsection{Developer time spent on a ticket}
 %-------------------------------------------------------------------------------
@@
 
-\begin{figure}[H]
+\begin{figure}[htbp]
   \centering
+  \includegraphics[width=70mm]{./images/devEvol.png}\\
   \includegraphics[width=70mm]{./images/devDefect.png}
-  \caption{Time spent by a developer to implement solution for  defects tickets}
-  \label{fig:devTimeDefect}
+  \caption{Time spent by a developer to implement his solution for  evolution (up) and defect (down) tickets}
+  \label{fig:devTimeDev}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/devEvol.png}
-  \caption{Time spent by a developer to implement solution for  evolution tickets}
-  \label{fig:devTimeEvol}
-\end{figure}
+%ressemble a closing time
+Figure \ref{fig:devTimeDev} presents the trend of closing time for evolution (up) and defect (down) tickets.
+One can notice a large variation of ploted time spent by the developer, even after smoothing it with the moving average.
 
-\subsubsection{Average time  to test a ticket after development}
+It takes longer (on average) to impement a solution for an evolution ticket than a defect ticket which seems natural.
+
+We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
+Finally we note that the closing time over the 15 years was multiplied by 1.5 for evolution tickets and 4 for defect tickets.
+This is an issue to investigate.
+\subsubsection{Time  to test a ticket after development}
 %-------------------------------------------------------------------------------
@@
 
- \begin{figure}[H]
+% constant pour defect -> OK
+% en diminution pour evolution -> peut-etre du a un manque de temps. Peut-etre cause d'une perte de quality et d' une augmentation des bugs
+
+ \begin{figure}[htbp]
   \centering
+  \includegraphics[width=70mm]{./images/evolutionTest.png} \\
   \includegraphics[width=70mm]{./images/timeDevTest.png}
-  \caption{Time spent by a developer to test his solution for  defect tickets}
-  \label{fig:devTimeTestBug}
+  \caption{Time spent by a developer to test his solution for  evolution (up) and defect (down) tickets}
+  \label{fig:devTimeTest}
 \end{figure}
+igure \ref{fig:devTimeTest} presents the trend of the time spent by a developer to test his solution for evolution (up) and defect (down) tickets.
+We can observe that the time spent for testing evolution tickets is decreasing. 
+This might be because developers lack to test evolution tickets. The lost of quality of the system and the growing number of defects  in the system may also be the reason.
+The time spent to test defects tickets is relativily constant which is ok.
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/evolutionTest.png}
-  \caption{Time spent by a developer to test his solution for  evolution tickets}
-  \label{fig:devTimeTestEvol}
-\end{figure}
-
- \subsubsection{Team Manager time estimation}
+\subsubsection{Time estimation}
  %-------------------------------------------------------------------------------
@@
 This estimation is based on the experience of the team manager.  
-We compare the time spent by the developer with the estimation per month over the life cycle of the system.  
+We ploted the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
 This is to assess if the developer has enough time to develop good quality source code.
 
-\begin{figure}[H]
+%2 periodes tres claires en quelle annee et du a un effort explicite pour mieux evaluer le temps qui est maintenant fait en interne par la manager.
+
+%avant on est audessus de 0 donc sous-estimation qui en plus est en croissance
+%apres en dessous donc sur-estimationde pire en pire pour les defauts mais de moins en moins pour les evolutionos avec une moyenne proche de 0
+
+\begin{figure}[htbp]
   \centering
+  \includegraphics[width=70mm]{./images/estimateEvol.png}\\
   \includegraphics[width=70mm]{./images/estimateBug.png}
-  \caption{Actual time spent by the developer minus time estimated by the manager for defect tickets.
-The yAxis represent the value of the gap between the development time and the estimated time in hour.
-The xAxis represent months from 2004 to 2019}
-  \label{fig:devEstDefect}
+  %\caption{Actual time spent by the developer minus time estimated by the manager for evolution tickets. 
+   % The yAxis represent the value of the gap between the development time and the estimated time in hour. 
+    %The xAxis represent months from 2004 to 2019}
+    \caption{Difference between time spent by a developer  and time estimated for  evolution (up) and defect (down) tickets}
+  \label{fig:devEst}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/estimateEvol.png}
-  \caption{Actual time spent by the developer minus time estimated by the manager for evolution tickets. 
-    The yAxis represent the value of the gap between the development time and the estimated time in hour. 
-    The xAxis represent months from 2004 to 2019}
-  \label{fig:devEstEvol}
-\end{figure}
+Figure \ref{fig:devEst} shows the trend  the difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
+One can notice two obvious periods of time. 
+ A period before may 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets . 
+ A period after may 2013  the time estimated is superior to the time spend by the developer ofr evolution and defect tickets.  
+ This estimate  is improving for evolution tickets as the regression line is closing to 0.
+But for defects tickets  the over estimation trend to increase.
 
-\section{Results and Discussion}
-%-------------------------------------------------------------------------------
-\label{sec:results-discussion}
+% \section{Discussion}
+% %-------------------------------------------------------------------------------
+% \label{sec:results-discussion}
 
-\begin{itemize}
-    \item Developers are now using subversion to integrate all their changes in the system. 
-    \item From 2004 to 2019, as we can see in figure \ref{fig:evol} and figure \ref{fig:defect} ,  the time to close a ticket is 5 times the time at 2004 for defects and 1.5 times for evolution.
-    \item Developers spend 4 times the time spent at 2004 for evolution tickets figure \ref{fig:devTimeEvol}, and  3 times for defects tickets figure \ref{fig:devTimeDefect}.
-    \item  Figure \ref{fig:devTimeTestEvol} and \ref{fig:devTimeTestBug} show that the developer spend in average 45 minutes test  the feature implemented of the fixed defect.
-    \item The time estimated by the developers team manager trend to be enough for the developer from 2013 for defects tickets and evolutions tickets.
-\end{itemize}
+% \begin{itemize}
+%     \item From 2004 to 2019, as we can see in figure \ref{fig:evol} and figure \ref{fig:defect} ,  the time to close a ticket is 5 times the time at 2004 for defects and 1.5 times for evolution.
+%     \item Developers spend 4 times the time spent at 2004 for evolution tickets figure \ref{fig:devTimeEvol}, and  3 times for defects tickets figure \ref{fig:devTimeDefect}.
+%     \item  Figure \ref{fig:devTimeTestEvol} and \ref{fig:devTimeTestBug} show that the developer spend in average 45 minutes test  the feature implemented of the fixed defect.
+%     \item The time estimated by the developers team manager trend to be enough for the developer from 2013 for defects tickets and evolutions tickets.
+% \end{itemize}
 
@@
 %\bibliographystyle{alpha}
-\bibliography{rmod,new}
+\bibliography{rmod,other,new}
 

### 2019-11-27 article.tex
fix mistakes

@@
 Software companies have little spare resources to allocate to software quality improvement or code defect removal.
-As a result they often develop features in a hurry.
+As a result, they often develop features in a hurry.
 As the system grows, it becomes harder and harder to maintain.
@@
 To ensure the future of the system, and through it, of the company itself, some re-engineering actions might be necessary.
-Long period of growth and evolution of the systems as well as staff evolution, lead to problems such as dead code, duplicate code, and obsolete documentation. 
+The long period of growth and evolution of the systems as well as staff evolution, lead to problems such as dead code, duplicate code, and obsolete documentation. 
 The developers at the origin of the application are no longer present, so a large part of the knowledge (and this at different levels of granularity) is scattered or lost.
@@
 This is the situation at CIM, a medium French company, which main business product we are studying.
-The system is written in an old language (PowerBuilder) typically unknown to young programmers which translates in a difficulty to hire new developpers.
-There is also a sense in the development team that the system suffers from architecture erosion and is difficult to maintain or evolve which translates into a steep learning curve for new developpers.
+The system is written in an old language (PowerBuilder) typically unknown to young programmers which translates in a difficulty to hire new developers.
+There is also a sense in the development team that the system suffers from architecture erosion and is difficult to maintain or evolve which translates into a steep learning curve for new developers.
 We are trying to help this company improve its software engineering practices and restructure the system to improve the situation.
@@
 For the reasons explained above, we cannot completely rely on current developers knowledge of the system.
-The only usable information about the system is its non versioned source code and a ticket database.
+The only usable information about the system is its non-versioned source code and a ticket database.
 Past literature often relied on historical data on the source code, for example
 cyclomatic complexity \cite{gill91}, or number of lines of code \cite{port18}.
-In lack of a reliable software versonning system, we could not use these solutions.
+In lack of a reliable software versioning system, we could not use these solutions.
 
@@
 
- This paper is structured as follows: we start with related work in the section \ref{sec:related-work}, followed by  the section \ref{sec:background}  in which we present ticket database mining background.
- In the section \ref{sec:methodology} we present our methodology. In section \ref{sec:results-discussion} we discussed our results and   conclude in section \ref{sec:conclusion}.
+ This paper is structured as follows: we start with related work in section \ref{sec:related-work}, followed by the section \ref{sec: background} in which we present tickets database mining background.
+ In the section \ref{sec:methodology} we present our methodology and conclude in section \ref{sec:conclusion}.
 
@@
 Software defect history and source code history are often used to monitor software maintenance or predict the system's quality. 
-For instance, software defect prediction using software repositories, has already been extensively discussed in literature as witnessed by many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
+For instance, software defect prediction using software repositories has already been extensively discussed in the literature as witnessed by many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
 %"intro": de quoi on va parler et pourquoi en parler ?
@@
 \cite{Herz13a} propose to consider ticket database.
-He reports that $33.8\%$ of the bugs studied among five open source projects were misclassified.
+He reports that $33.8\%$ of the bugs studied among five open-source projects were misclassified.
 For this reason, other researchers try to automatically re-classify maintenance activities (e.g. \cite{Mock20a,Levin19a}).
@@
 The largest library is over 300 KLOC.
-The development team varied over time but counts 15 people at the moment, without the testing team which is external to developpement.
+The development team varied over time but counts 15 people at the moment, without the testing team which is external to development.
 
-PowerBuilder version supports version control only since its 2017 version, and even this supports is still not entirelly satisfying, for example
+PowerBuilder version supports version control only since its 2017 version, and even this supports is still not entirely satisfying, for example
 conflict resolution is performed automatically by the system by choosing one version over the other without asking the developer.
@@
 At CIM, tickets are stored in the tickets database since 2000.
-A ticket represent a unit work.
-The ticket database drives the entire software evolution process: assignement of work to developers, management of the workflow to answer a client request, billing information about each task.
-There are tickets for fixing defects, writing documentation, adding new feature, etc. 
-As a consequence we can rely on a ticket's classification because it is reviewed by the team manager to ensure that it is properly handled.
+A ticket represents a unit work.
+The ticket database drives the entire software evolution process: assignment of work to developers, management of the workflow to answer a client request, billing information about each task.
+There are tickets for fixing defects, writing documentation, adding new features, etc. 
+As a consequence, we can rely on a ticket's classification because it is reviewed by the team manager to ensure that it is properly handled.
+
+At CIM, a ticket includes the following characteristics among other things:
 
@@
 Our long-term goal is to help developers re-engineer the system at a small cost.
-This is need to improve the general quality and make future evolution easier, but it need to be cheap to convince upper management investing in this purely technical task.
+This is needed to improve the general quality and make future evolution easier, but it needs to be cheap to convince upper management investing in this purely technical task.
 
-Therefore, we need to validate our intervention as well as the restructuring work developpers might engage into in the future.
+Therefore, we need to validate our intervention as well as the restructuring work developers might engage in the future.
 
@@
 Our first action was to introduce a version management system.
-We chose  Subversion (SVN) because it was simpler to explain to developpers that were not familiar with the concepts of version management.
-We gave a short formation to the developpers and they are now starting to use it as part of the new process.
+We chose Subversion (SVN) because it was simpler to explain to developers that were not familiar with the concepts of version management.
+We gave a short training session to the developers, and they are now starting to use it as part of the new process.
 
-In addition we are recontructing a summarized source history in SVN by importing one after the other the different major versions curently stored in directories (versions 2012 to 2019). 
-We hope that this will help us analyse the system historical code changes in order to have additionnal information about th system evolution.
+Besides, we are reconstructing a summarized source history in SVN by importing one after the other the different major versions currently stored in directories (versions 2012 to 2019). 
+We hope that this will help us analyze the system's historical code changes to have additional information about the system evolution.
 
@@
 
-Our goal was to characterize the system to be able to measure our impact and that of the developpers in the future.
+Our goal was to characterize the system to be able to measure our impact and that of the developers in the future.
 The problem was to extract information from the system that was relevant for the company and for which we could hope to have some impact.
@@
  \item How long does it take to close a ticket?
- \item Developement time spent on a ticket?
+ \item Development time spent on a ticket?
  \item Testing time spent by the developer on a ticket?
- \item Testing time spent by the tester (other team) on a ticket?
+ \item Testing time spent by the tester (other teams) on a ticket?
  \item Difference between the time estimated and the actual time for a ticket?
@@
   \item Tickets may concern several software systems in the company and different development teams.
-  We thus selected tickets related to the system we are studing.
+  We thus selected tickets related to the system we are studying.
 
   \item The ticket database contains data from 1998  until today. 
-  Before 2004, tickets information is not always consistent, for example, missing creation date or missing/incorrect category.
+  Before 2004, tickets information are not always consistent, for example, missing creation date or missing/incorrect category.
   This constrained us to eliminate tickets prior to 2004.
@@
   A simple and frequent case is two swapped characters \emph{cwm\_liq\_ou} instead of \emph{cwm\_liq\_uo} (``uo'' PowerBuilder User Object).
-  Some more complex cases require an understanding of the application domain and the system, for example \emph{uo\_liq} instead of \emph{cwm\_liq\_uo}.
+  Some more complex cases require an understanding of the application domain and the system, for example, \emph{uo\_liq} instead of \emph{cwm\_liq\_uo}.
   We identified all the errors manually and corrected them.
 
-  \item The category of the ticket is fine grained whereas we are only interest in evolution versus corrective tickets.
-  In our analysis we recategorize the tickets according to some simple dictionnary provided by the team manager.
+  \item The category of the ticket is fine-grained whereas we are only interested in evolution versus corrective tickets.
+  In our analysis, we recategorize the tickets according to some simple dictionary provided by the team manager.
 
@@
 
-We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (non stationary results) than made it diffcult to interpret the graphs.
-To get smoother plots, we finally computed the moving average of [month-2 ; month+2] for each month.
-Therefore, ploted data for july 2010 of any time metric correspond to average time of all tickets opened between may 2010 (inclusive) and september 2010 (inclusive).
+We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (nonstationary results) than made it challenging to interpret the graphs.
+To get smoother plots, we finally computed the moving average of [month-2; month+2] for each month.
+Therefore, plotted data for July 2010 of any time metric correspond to the average time of all tickets opened between May 2010 (inclusive) and September 2010 (inclusive).
 
-Finally to get a better notion of the trend, we will also plot the linear regression of the curve for each graph.
+Finally, to get a better notion of the trend, we will also plot the linear regression of the curve for each graph.
 
@@
 We note that 56\% of defect tickets seems a high proportion.
-Literature (e.g. \cite{Pigo96a}) states that the proportion is typically 20\% to 25\% of defect tickets.
+Literature (e.g. \cite{Pigo96a} ) states that the proportion is typically 20\% to 25\% of defect tickets.
 This is an issue that we will investigate and monitor in the future.
@@
 Figure \ref{fig:closingTime} presents the trend of closing time for evolution (up) and defect (down) tickets.
-One can notice a large variation of ploted closing time, even after smoothing it with the moving average.
+One can notice a large variation of plotted closing time, even after smoothing it with the moving average.
 It does not seem to be a problem.
@@
 
-When a developer work on the task assign to in a ticket, he spend time to analyse  the task. 
-He then implement a solution and then test.
- The time spend analyzing and implementing the task assign in a ticket depend on the workload  of the ticket, the complexity of system, etc.  
+When a developer work on the task assigns to in a ticket, he spent time to analyze the task. 
+He then implements a solution and then tests.
+ The time spent analyzing and implementing the task assign in a ticket depending on the workload of the ticket, the complexity of the system, etc.  
 We compute the average time spent by developers per month. 
-The data also present rapid up-and-down variation, which we smooth with simple moving average of period 4. We use  linear regression to fit the data.
+The data also present rapid up-and-down variation, which we smooth with a simple moving average of period 4. We use linear regression to fit the data.
 
@@
 Figure \ref{fig:devTimeDev} presents the trend of closing time for evolution (up) and defect (down) tickets.
-One can notice a large variation of ploted time spent by the developer, even after smoothing it with the moving average.
+One can notice a large variation of plotted time spent by the developer, even after smoothing it with the moving average.
 
-It takes longer (on average) to impement a solution for an evolution ticket than a defect ticket which seems natural.
+It takes longer (on average) to implement a solution for an evolution ticket than a defect ticket which seems natural.
 
 We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
-Finally we note that the closing time over the 15 years was multiplied by 1.5 for evolution tickets and 4 for defect tickets.
+Finally, we note that the closing time over the 15 years was multiplied by 1.5 for evolution tickets and 4 for defect tickets.
 This is an issue to investigate.
@@
 \end{figure}
-igure \ref{fig:devTimeTest} presents the trend of the time spent by a developer to test his solution for evolution (up) and defect (down) tickets.
-We can observe that the time spent for testing evolution tickets is decreasing. 
+Figure \ref{fig:devTimeTest} presents the trend of the time spent by a developer to test his solution for evolution (up) and defect (down) tickets.
+We can observe that the time spent on testing evolution tickets is decreasing. 
 This might be because developers lack to test evolution tickets. The lost of quality of the system and the growing number of defects in the system may also be the reason.
-The time spent to test defects tickets is relativily constant which is ok.
+The time spent to test defects tickets is relatively constant which is ok.
 
@@
 This estimation is based on the experience of the team manager.  
-We ploted the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
+We plotted the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
 This is to assess if the developer has enough time to develop good quality source code.
@@
 Figure \ref{fig:devEst} shows the trend the difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
-One can notice two obvious periods of time. 
- A period before may 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets . 
- A period after may 2013  the time estimated is superior to the time spend by the developer ofr evolution and defect tickets.  
+One can notice two obvious periods. 
+ A period before may 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets. 
+ A period after May 2013 the time estimated is superior to the time spent by the developer for evolution and defect tickets. 
  This estimate is improving for evolution tickets as the regression line is closing to 0.
-But for defects tickets  the over estimation trend to increase.
+But for defects tickets the overestimation trend to increase.
 
@@
 
-In this paper we present our first step in  improving practices in a french company. We first introduce subversion, a version control system.
-The developers team is now using it and the software studied source code is now versioned.
-This open the door for further analysis of the code repository to understand the system evolution. 
+In this paper, we present our first step in improving practices in a french company. We first introduce subversion, a version control system.
+The developers' team is now using it and the software studied source code is now versioned.
+This opens the door for further analysis of the code repository to understand the system evolution. 
 Using the ticket database, the moving average and regression line, we build a defect model mainly assess the developer effort throughout the project life cycle.
-We will use this model to monitor our future actions which is: how to decompose the system big methods.
+We will use this model to monitor our future actions which are: how to decompose the system big methods.
 \bibliographystyle{plainnat}

### 2019-11-28 __latexindent_temp.tex
update the article

@@
 
- This paper is structured as follows: we start with related work in the section \ref{sec:related-work}, followed by  the section \ref{sec:defectModel}  in which we present ticket database mining background.
- In the section 4 we present our results and validation. We  conclude in section 5.
+ This paper is structured as follows: we start with related work in section \ref{sec:related-work}, followed by the section \ref{sec:background} in which we present tickets database mining background.
+ In the section \ref{sec:methodology} we present our methodology and conclude in section \ref{sec:conclusion}.
 
@@
 
-Other researchers considered ticket database to characterize a system.
+\cite{Herz13a} propose to consider ticket database.
+He reports that $33.8\%$ of the bugs studied among five open-source projects were misclassified.
+For this reason, other researchers try to automatically re-classify maintenance activities (e.g. \cite{Mock20a,Levin19a}).
+
+%Other researchers considered ticket database to characterize a system. For instance, \cite{Levin19a} 
+At CIM, maintenance activities classification is more reliable because it drives the entire software evolution process.
+We rely on this classification to make our analysis.
 
@@
 %-------------------------------------------------------------------------------
-\label{sec:defectModel}
+\label{sec:background}
 
@@
 
-\subsection{Presentation of the studied system}
+\subsection{Presentation of the system studied}
 %-------------------------------------------------------------------------------
@@
 Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
-This is the case of the system we are studying which is older than 20 years. 
-It's a 3 MLOC software written in Powerbuilder.
-
+This is the case of the system we are studying which is more than 20 years old. 
+It is written in Powerbuilder.
 Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
@@
 A Powerbuilder library contains differents type of objects: datawindow, user object, global function, menu, etc. 
-Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
-Its 2017 version  supports version control but for historical reasons it was never used on the system studied.% and the support is not stable.
+Powerbuilder is a procedural language that evolved to (partial) object-orientedness: inheritance and object-oriented features are limited to some object types (windows, user objects and menus).
 
-With 117 Powerbuilder libraries, the  bigest library is  over 300 KLOC.
-The system is not versioned in a version control system but some old major versions or archivied in separate directories.
-Old versions (before 2012) are completely lost.
+The system has 3 MLOC, in 117 Powerbuilder libraries.
+The largest library is over 300 KLOC.
+The development team varied over time but counts 15 people at the moment, without the testing team which is external to development.
+
+PowerBuilder version supports version control only since its 2017 version, and even this supports is still not entirely satisfying, for example
+conflict resolution is performed automatically by the system by choosing one version over the other without asking the developer.
+For these reasons, version control management was never used on the system studied.% and the support is not stable. 
+However some old major versions or archived in separate directories.
+Versions before 2012 are completely lost.
+Some version control is done informally inside the team.
+When developers work on the same version of the system, they chat with each other to notify which part they are modifying so that others won't modify the same part.
+Also, each developer has to write a comment in the source code with his/her name and the date the modification he/she performed. 
+%We believe that writing author in a comment in the source can be easily handled by a version control system.
 
@@
 %-------------------------------------------------------------------------------
+% depuis quand ?
+% tres important car utilise dans toute la boite: affectatin du travail, workflow, facturation
 
-A ticket is related do a task to do and it is used for billing. 
-This task can be fixing a defect, writing documentation, adding a new feature, etc. 
-Once the task is done and validated, the ticket is close.
-At CIM, a ticket has the following characteristics:
+At CIM, tickets are stored in the tickets database since 2000.
+A ticket represents a unit work.
+The ticket database drives the entire software evolution process: assignment of work to developers, management of the workflow to answer a client request, billing information about each task.
+There are tickets for fixing defects, writing documentation, adding new features, etc. 
+As a consequence, we can rely on a ticket's classification because it is reviewed by the team manager to ensure that it is properly handled.
+
+At CIM, a ticket includes the following characteristics among other things:
+
+At CIM, a ticket includes the following characteristics among other things:
 
@@
 \item the closing date
-\item the library(ies) it is related to
+\item the estimation of the time needed by the developer to work on the ticket
 \item time spent by a developer
@@
   \end{itemize}
-\item  the estimation of the time needed by the developer to work on the ticket
+  \item the library(ies) impacted
 \end{itemize}
-In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.
-
-\subsection{Moving average}
-%-------------------------------------------------------------------------------
-
-A moving average is a statistic technical usually used to smooth a time series data and estimate it trend \cite{MOLU17}.
- The moving average of a period m is a series of consecutive averages of m terms at a time. 
- The simple moving average is calculated as:
-
-\begin{equation}
-SMA_{t+1}=\frac{\sum\limits_{i=t-m}^t X_i}{m}
-\end{equation}
 
@@
 
-We collected data  from the company Tickets database .  
-Then we proceed to data cleaning.
-The data analytic process is guided by the following research methodology:
+Our long-term goal is to help developers re-engineer the system at a small cost.
+This is needed to improve the general quality and make future evolution easier, but it needs to be cheap to convince upper management investing in this purely technical task.
+
+Therefore, we need to validate our intervention as well as the restructuring work developers might engage in the future.
+
+\subsection{Souce code versionning}
+%-------------------------------------------------------------------------------
+
+Our first action was to introduce a version management system.
+We chose Subversion (SVN) because it was simpler to explain to developers that were not familiar with the concepts of version management.
+We gave a short training session to the developers, and they are now starting to use it as part of the new process.
+
+Besides, we are reconstructing a summarized source history in SVN by importing one after the other the different major versions currently stored in directories (versions 2012 to 2019). 
+We hope that this will help us analyze the system's historical code changes to have additional information about the system evolution.
+
+\subsection{Ticket data analysis}
+%-------------------------------------------------------------------------------
+
+Our goal was to characterize the system to be able to measure our impact and that of the developers in the future.
+The problem was to extract information from the system that was relevant for the company and for which we could hope to have some impact.
+All this within the very restricted context described above.
+
+We turned to the ticket database and elected the following questions:
 \begin{itemize}
-\item Pose a problem
-\item Make experimentation on data
-\item Validation of results
+ \item What is the proportion of evolution versus correction tickets?
+ \item How long does it take to close a ticket?
+ \item Development time spent on a ticket?
+ \item Testing time spent by the developer on a ticket?
+ \item Testing time spent by the tester (other teams) on a ticket?
+ \item Difference between the time estimated and the actual time for a ticket?
  \end{itemize}
 
-\subsection{Data collection and data cleaning}
+%a revoir
+
+The ticket database first needed some cleaning:
+\begin{itemize}
+  \item Tickets may concern several software systems in the company and different development teams.
+  We thus selected tickets related to the system we are studying.
+
+  \item The ticket database contains data from 1998  until today. 
+  Before 2004, tickets information are not always consistent, for example, missing creation date or missing/incorrect category.
+  This constrained us to eliminate tickets prior to 2004.
+
+  \item Up to recently, the name of the library concerned by a ticket was filled manually (free text).
+  As a consequence, there are some typos in the names that need to be corrected.
+  A simple and frequent case is two swapped characters \emph{cwm\_liq\_ou} instead of \emph{cwm\_liq\_uo} (``uo'' PowerBuilder User Object).
+  Some more complex cases require an understanding of the application domain and the system, for example, \emph{uo\_liq} instead of \emph{cwm\_liq\_uo}.
+  We identified all the errors manually and corrected them.
+
+  \item The category of the ticket is fine-grained whereas we are only interested in evolution versus corrective tickets.
+  In our analysis, we recategorize the tickets according to some simple dictionary provided by the team manager.
+
+\end{itemize}
+
+For all the time questions, the tickets are grouped by month of creation and their value (for example time to close the ticket) are averaged for the month of creation.  
+We compute the data for our questions as follows:
+\begin{itemize}
+  \item We compute the \emph{closing time} of a ticket simply as the time between creation and closing of each (closed) ticket.
+\item  The time spent by the developers to implement ist's solution for a ticket is provided in this format: \emph{//number of days//number of hours//number of minute//}.
+ We convert this format into duration for each tickets. 
+ \item When a developer finishes a development related to a ticket, he tests his solution.  
+ The testing time is recorded in the ticket database in the format \emph{//number of days//number of hours//number of minute//}.
+  We convert this information in duration and plotted it.
+ \item For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
+ This estimation is based on the experience of the team manager.  
+ We plotted the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
+ This is to assess if the developer has enough time to develop quality source code.
+ %autre metric
+\end{itemize}
+
+We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (nonstationary results) that made it hard to interpret the graphs.
+To get smoother plots, we computed the moving average of [month-2; month+2] for each month.
+Therefore, plotted data for July 2010 of any time metric correspond to the average time of all tickets opened between May 2010 (inclusive) and September 2010 (inclusive).
+
+Finally, to get a better notion of the trend, we will also plot the linear regression of the curve for each graph.
+
+\subsection{Results}
 %-------------------------------------------------------------------------------
 
-The ticket database contains data from 1998  until 2019. 
-This data includes tickets  different teams and software in  the company. 
-In the field related to the  library a ticket is related to,  the name of the library is not always well written.
-
-We use tickets database data from 2004 to 2019 . 
-We  remove all tickets, not related  to the studied system and reformat duration per ticket.
-By interviewing developers, we categorize tickets into two sets: tickets related to defects and tickets related to evolution.
-
- \subsection{Questions}
- \begin{itemize}
- \item How to avoid the system source code lost?
- \item What is the number of defect per library?
- \item How long on average, does it take to open and close a ticket?
- \item How long on average,  does a developer spend on a ticket ?
- \item How long on average, does a developer spend to test a ticket after development ?
- \item Does the team manager estimate well  the time needed by the developer?
- \item If the time estimated by the team manager is good, does the developer finish because  of time constraint?
- \end{itemize}
-
- \subsection{Experimentation}
-
-\subsubsection{Avoid the system source code lost}
+\subsection{Souce code versionning}
 %-------------------------------------------------------------------------------
 
-The system source code is not versioned.  Some versions of the system are lost. 
-When developers work in the same version of the system, they chat with each other to notify which part of the system they are modifying so that others won't modify the same part to avoid losing modifications.
-Besides, each developer has to write in a comment in the source code his name and the date in the form of each modification he made.
-We believe that writing author in a comment in the source can be easily handled by a version control system.
-This is because of Powerbuilder support version controlling system from the 2017 release. 
-The support provided by Powerbuilder is not stable.
-The conflict resolution option is limited and a simple copy-paste of a library require a huge walk-around to update files. 
-With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion.
+The introduction of SVN only started one month ago and we do not have yet significant results to report.
 
- \subsubsection{Number of defects per library}
+For the reconstruction of the summarized source history, we already imported major versions until 2015 in a separated repository. 
+ %We then grouped them by major release. 
+ %We create an SVN repository in which we create a branch for each major release. We are pushing each release in the branch  of the major release it belong to.
+
+\subsubsection{Data collection}
 %-------------------------------------------------------------------------------
 
-We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolution.
-This give us an overview of defect  history per library. And  which libraries   trend to have defects.
+\begin{table}[htbp]
+  \begin{center}
+    \caption{Ticket analysed}
+    \label{tab:proportion}
+    \begin{tabular}{| l | c |c|}
+      \hline
+      Tickets & Defect  & Evolution  \\
+      \hline
+      27380&15407 ($56\%$)&11973 (44\%)\\
+      \hline 
+    \end{tabular}
+  \end{center}  
+\end{table}
 
-\subsubsection{ Average time to open and close a ticket}
+Table \ref{tab:proportion} gives the number of defect versus evolution tickets.
+We note that 56\% of defect tickets seems a high proportion.
+Literature (e.g. \cite{Pigo97a} ) states that the proportion is typically 20\% to 25\% of defect tickets.
+This is an issue that we will investigate and monitor in the future.
+
+\subsubsection{Time to close a ticket}
 %-------------------------------------------------------------------------------
 
-A ticket is closed when the task it is related to is done and validated. 
-We use the time a ticket remains open over the life cycle of the studied system as an indicator of the system state. 
-We grouped tickets by the month of creation.
-We then compute the average of  the duration between the time when the ticket is created and the time when the ticket is closed for each month.  
-We do this for tickets categorized as defect and tickets categorized as evolution. 
-We finally plot the result of each category into a graph.  First, the plot exhibits rapid up-and-down variation.
-We could not derive any trend from this variation. 
-We smooth the plot using the simple moving average of period 4 on the data.  
-We then plot the linear regression to fit the data.  
-The figure \ref{fig:evol} presents the trend of time to close evolution ticket and  the figure \ref{fig:defect} shows  the trends  of time to close defects tickets.
-
-\begin{figure}[H]
+\begin{figure}[htbp]
   \centering
-  \includegraphics[width=70mm]{./images/openCloseEvol.png}
-  \caption{Time to close evolution tickets}
-  \label{fig:evol}
+  \includegraphics[width=70mm]{./images/openCloseEvol.png} \\
+  \includegraphics[width=70mm]{./images/openCloseBug.png}
+  \caption{Time to close evolution (up) and defect (down) tickets}
+  \label{fig:closingTime}
 \end{figure}
 
-\begin{figure}[H]
+Figure \ref{fig:closingTime} presents the trend of closing time for evolution (up) and defect (down) tickets.
+One can notice a large variation of plotted time, even after smoothing it with the moving average.
+
+It takes longer (on average) to close an evolution ticket than a defect ticket which seems natural.
+
+We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
+Finally we note that the closing time over the 15 years was multiplied by 2 for evolution tickets and 3 for defect tickets.
+Again this is an issue to investigate.
+
+\subsubsection{Developer time spent on a ticket}
+%-------------------------------------------------------------------------------
+
+When a developer works on a ticket, he spent time to analyze the task. 
+He then implements a solution and then tests.
+ The time spent analyzing and implementing solution for the ticket depends on the workload of the ticket, the complexity of the system, etc.
+
+\begin{figure}[htbp]
   \centering
-  \includegraphics[width=70mm]{./images/openCloseBug.png}
-  \caption{Time to close defects tickets}
-  \label{fig:defect}
+  \includegraphics[width=70mm]{./images/devEvol.png}\\
+  \includegraphics[width=70mm]{./images/devDefect.png}
+  \caption{Time spent by a developer to implement his solution for  evolution (up) and defect (down) tickets}
+  \label{fig:devTimeDev}
 \end{figure}
 
-\subsubsection{Time developer spend on a ticket }
+%ressemble a closing time
+Figure \ref{fig:devTimeDev} presents the trend of closing time for evolution (up) and defect (down) tickets.
+One can notice a large variation of plotted time spent by the developer, even after smoothing it with the moving average.
+
+It takes longer (on average) to implement a solution for an evolution ticket than a defect ticket which seems natural.
+
+We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
+Finally, we note that the closing time over the 15 years was multiplied by 1.5 for evolution tickets and 4 for defect tickets.
+This is an issue to investigate.
+\subsubsection{Time  to test a ticket after development}
 %-------------------------------------------------------------------------------
 
-When a developer work on the task assign to in a ticket, he spend time to analyse  the task. 
-He then implement a solution and then test.
- The time spend analyzing and implementing the task assign in a ticket depend on the workload  of the ticket, the complexity of system, etc.  
-We compute the average time spent by developers per month. 
-The data also present rapid up-and-down variation, which we smooth with simple moving average of period 4. We use  linear regression to fit the data.
+% constant pour defect -> OK
+% en diminution pour evolution -> peut-etre du a un manque de temps. Peut-etre cause d'une perte de quality et d' une augmentation des bugs
 
-\begin{figure}[H]
+ \begin{figure}[htbp]
   \centering
-  \includegraphics[width=70mm]{./images/devDefect.png}
-  \caption{Time spent by a developer to implement solution for  defects tickets}
-  \label{fig:devTimeDefect}
+  \includegraphics[width=70mm]{./images/evolutionTest.png} \\
+  \includegraphics[width=70mm]{./images/timeDevTest.png}
+  \caption{Time spent by a developer to test his solution for  evolution (up) and defect (down) tickets}
+  \label{fig:devTimeTest}
+\end{figure}
+Figure \ref{fig:devTimeTest} presents the trend of the time spent by a developer to test his solution for evolution (up) and defect (down) tickets.
+We can observe that the time spent on testing evolution tickets is decreasing. 
+This might be because developers lack to test evolution tickets. The lost of quality of the system and the growing number of defects in the system may also be the reason.
+The time spent to test defects tickets is relatively constant which is ok.
+
+\subsubsection{Time estimation}
+ %-------------------------------------------------------------------------------
+
+%2 periodes tres claires en quelle annee et du a un effort explicite pour mieux evaluer le temps qui est maintenant fait en interne par la manager.
+
+%avant on est audessus de 0 donc sous-estimation qui en plus est en croissance
+%apres en dessous donc sur-estimationde pire en pire pour les defauts mais de moins en moins pour les evolutionos avec une moyenne proche de 0
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=70mm]{./images/estimateEvol.png}\\
+  \includegraphics[width=70mm]{./images/estimateBug.png}
+  %\caption{Actual time spent by the developer minus time estimated by the manager for evolution tickets. 
+   % The yAxis represent the value of the gap between the development time and the estimated time in hour. 
+    %The xAxis represent months from 2004 to 2019}
+    \caption{Difference between time spent by a developer  and time estimated for  evolution (up) and defect (down) tickets}
+  \label{fig:devEst}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/devEvol.png}
-  \caption{Time spent by a developer to implement solution for  evolution tickets}
-  \label{fig:devTimeEvol}
-\end{figure}
+Figure \ref{fig:devEst} shows the trend the difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
+One can notice two obvious periods. 
+ A period before may 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets. 
+ A period after May 2013 the time estimated is superior to the time spent by the developer for evolution and defect tickets. 
+ This estimate is improving for evolution tickets as the regression line is closing to 0.
+But for defects tickets the overestimation trend to increase.
 
-\subsubsection{Average time  to test a ticket after development}
-%-------------------------------------------------------------------------------
+% \section{Discussion}
+% %-------------------------------------------------------------------------------
+% \label{sec:results-discussion}
 
-Generally, when a developer finishes a development related to a ticket, he tests his solution.  
-The testing time is recorded in the ticket database.
- We use this information to compute the average per month of testing time.
-
- \begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/timeDevTest.png}
-  \caption{Time spent by a developer to test his solution for  defect tickets}
-  \label{fig:devTimeTestBug}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/evolutionTest.png}
-  \caption{Time spent by a developer to test his solution for  evolution tickets}
-  \label{fig:devTimeTestEvol}
-\end{figure}
-
- \subsubsection{Team Manager time estimation}
- %-------------------------------------------------------------------------------
-
-For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
-This estimation is based on the experience of the team manager.  
-We compare the time spent by the developer with the estimation per month over the life cycle of the system.  
-This is to assess if the developer has enough time to develop good quality source code.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/estimateBug.png}
-  \caption{Actual time spent by the developer minus time estimated by the manager for defect tickets.
-The yAxis represent the value of the gap between the development time and the estimated time in hour.
-The xAxis represent months from 2004 to 2019}
-  \label{fig:devEstDefect}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=70mm]{./images/estimateEvol.png}
-  \caption{Actual time spent by the developer minus time estimated by the manager for evolution tickets. 
-    The yAxis represent the value of the gap between the development time and the estimated time in hour. 
-    The xAxis represent months from 2004 to 2019}
-  \label{fig:devEstEvol}
-\end{figure}
-
-\section{Results and Discussion}
-%-------------------------------------------------------------------------------
-\label{sec:results-discussion}
-
-\begin{itemize}
-    \item Developers are now using subversion to integrate all their changes in the system. 
-    \item From 2004 to 2019, as we can see in figure \ref{fig:evol} and figure \ref{fig:defect} ,  the time to close a ticket is 5 times the time at 2004 for defects and 1.5 times for evolution.
-    \item Developers spend 4 times the time spent at 2004 for evolution tickets figure \ref{fig:devTimeEvol}, and  3 times for defects tickets figure \ref{fig:devTimeDefect}.
-    \item  Figure \ref{fig:devTimeTestEvol} and \ref{fig:devTimeTestBug} show that the developer spend in average 45 minutes test  the feature implemented of the fixed defect.
-    \item The time estimated by the developers team manager trend to be enough for the developer from 2013 for defects tickets and evolutions tickets.
-\end{itemize}
+% \begin{itemize}
+%     \item From 2004 to 2019, as we can see in figure \ref{fig:evol} and figure \ref{fig:defect} ,  the time to close a ticket is 5 times the time at 2004 for defects and 1.5 times for evolution.
+%     \item Developers spend 4 times the time spent at 2004 for evolution tickets figure \ref{fig:devTimeEvol}, and  3 times for defects tickets figure \ref{fig:devTimeDefect}.
+%     \item  Figure \ref{fig:devTimeTestEvol} and \ref{fig:devTimeTestBug} show that the developer spend in average 45 minutes test  the feature implemented of the fixed defect.
+%     \item The time estimated by the developers team manager trend to be enough for the developer from 2013 for defects tickets and evolutions tickets.
+% \end{itemize}
 
@@
 
-In this paper we present our first step in  improving practices in a french company. We first introduce subversion, a version control system.
-The developers team is now using it and the software studied source code is now versioned.
-This open the door for further analysis of the code repository to understand the system evolution. 
+In this paper, we present our first step in improving practices in a french company. We first introduce subversion, a version control system.
+The developers' team is now using it and the software studied source code is now versioned.
+This opens the door for further analysis of the code repository to understand the system evolution. 
 Using the ticket database, the moving average and regression line, we build a defect model mainly assess the developer effort throughout the project life cycle.
-We will use this model to monitor our future actions which is: how to decompose the system big methods.
+We will use this model to monitor our future actions which are: how to decompose the system big methods.
 \bibliographystyle{plainnat}
 %\bibliographystyle{alpha}
-\bibliography{rmod,new}
+\bibliography{rmod,other,new}
 

### 2019-11-28 article.tex
update the article

@@
 
-This is the situation at CIM, a medium French company, which main business product we are studying.
+This is the situation at medium French company, which main business product we are studying.
 The system is written in an old language (PowerBuilder) typically unknown to young programmers which translates in a difficulty to hire new developers.
@@
 
- This paper is structured as follows: we start with related work in section \ref{sec:related-work}, followed by the section \ref{sec: background} in which we present tickets database mining background.
+ This paper is structured as follows: we start with related work in section \ref{sec:related-work}, followed by the section \ref{sec:background} in which we present tickets database mining background.
  In the section \ref{sec:methodology} we present our methodology and conclude in section \ref{sec:conclusion}.
@@
 %Other researchers considered ticket database to characterize a system. For instance, \cite{Levin19a} 
-At CIM, maintenance activities classification is more reliable because it drives the entire software evolution process.
+At the company, maintenance activities classification is more reliable because it drives the entire software evolution process.
 We rely on this classification to make our analysis.
@@
 
-At CIM, tickets are stored in the tickets database since 2000.
+At the company, tickets are stored in the tickets database since 2000.
 A ticket represents a unit work.
@@
 
-At CIM, a ticket includes the following characteristics among other things:
+At the company, a ticket includes the following characteristics among other things:
 
-At CIM, a ticket includes the following characteristics among other things:
+At the company, a ticket includes the following characteristics among other things:
 
@@
   In our analysis, we recategorize the tickets according to some simple dictionary provided by the team manager.
+  \item Duration are registered in the following string format : \emph{//number\_of\_days//number\_of\_hours//number\_of\_minute//}.
+   For example \emph{//1j//2h//00//}  (one day two hours), is the same as \emph{//1 jour//2h//}.
+  Sometimes the format is not respected . For example \emph{5 jours } or \emph{5 g} is registered instead of \emph{//5j//00//00//}.
+  We create a simple  converter which covers all the cases and convert them into duration.
 
@@
 \begin{itemize}
+
   \item We compute the \emph{closing time} of a ticket simply as the time between creation and closing of each (closed) ticket.
-\item %autre metric
+
+  \item  The time spent by the developers to implement its solution for a ticket is provided in the format (\emph{//number\_of\_days//number\_of\_hours//number\_of\_minute//}).
+ We convert this format into duration for each tickets.
+
+ \item The testing time is recorded in the ticket database in the format (\emph{//number\_of\_days//number\_of\_hours//number\_of\_minute//}).
+  We convert this information in duration.
+
+ \item For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
+ This estimation is based on the experience of the team manager.  
+ We compute the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
+ %autre metric
 \end{itemize}
 
-We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (nonstationary results) than made it challenging to interpret the graphs.
-To get smoother plots, we finally computed the moving average of [month-2; month+2] for each month.
+We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (nonstationary results) that made it hard to interpret the graphs.
+To get smoother plots, we computed the moving average of [month-2; month+2] on each month.
 Therefore, plotted data for July 2010 of any time metric correspond to the average time of all tickets opened between May 2010 (inclusive) and September 2010 (inclusive).
@@
 
-\subsection{Souce code versionning}
+\subsubsection{Souce code versionning}
 %-------------------------------------------------------------------------------
 
-The introduction of SVN only started one month ago and we do not have yet significant results to report here.
+The introduction of SVN only started one month ago and we do not have yet significant results to report.
 
-For the reconstruction of the summarized source history, we already imported major versions until 2015 in a separated repository. 
+For the reconstruction of the summarized source history, we already imported major versions sorted by release date until 2015 in an SVN repository. 
+At the end of the importing we could analyze changes between release at source code level.
  %We then grouped them by major release. 
@@
 Figure \ref{fig:closingTime} presents the trend of closing time for evolution (up) and defect (down) tickets.
-One can notice a large variation of plotted closing time, even after smoothing it with the moving average.
-It does not seem to be a problem.
+One can notice a large variation of plotted time, even after smoothing it with the moving average. 
+We don't see it as a pointing to a significant problem with the system.
 
@@
 
-When a developer work on the task assigns to in a ticket, he spent time to analyze the task. 
+When a developer works on a ticket, he spent time to analyze the task. 
 He then implements a solution and then tests.
- The time spent analyzing and implementing the task assign in a ticket depending on the workload of the ticket, the complexity of the system, etc.  
-We compute the average time spent by developers per month. 
-The data also present rapid up-and-down variation, which we smooth with a simple moving average of period 4. We use linear regression to fit the data.
+ The time spent analyzing and implementing solution for the ticket depends on the workload of the ticket, the complexity of the system, etc.
 
@@
 Figure \ref{fig:devTimeDev} presents the trend of closing time for evolution (up) and defect (down) tickets.
-One can notice a large variation of plotted time spent by the developer, even after smoothing it with the moving average.
+As Figure \ref{fig:closingTime}, Figure \ref{fig:devTimeDev} show a large variation even after smoothing.
 
@@
 %-------------------------------------------------------------------------------
-
-Generally, when a developer finishes a development related to a ticket, he tests his solution.  
-The testing time is recorded in the ticket database.
- We use this information to compute the average per month of testing time.
 
@@
 \end{figure}
+When a developer finishes a development related to a ticket, he tests his solution.  
 Figure \ref{fig:devTimeTest} presents the trend of the time spent by a developer to test his solution for evolution (up) and defect (down) tickets.
 We can observe that the time spent on testing evolution tickets is decreasing. 
-This might be because developers lack to test evolution tickets. The lost of quality of the system and the growing number of defects in the system may also be the reason.
+This might be because developers lack time to  test evolution tickets. 
+The lost of quality of the system and the growing number of defects in the system may be due to lack of tests.
 The time spent to test defects tickets is relatively constant which is ok.
@@
  %-------------------------------------------------------------------------------
-
-For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
-This estimation is based on the experience of the team manager.  
-We plotted the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
-This is to assess if the developer has enough time to develop good quality source code.
 
@@
 
-Figure \ref{fig:devEst} shows the trend the difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
-One can notice two obvious periods. 
- A period before may 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets. 
- A period after May 2013 the time estimated is superior to the time spent by the developer for evolution and defect tickets. 
+Figure \ref{fig:devEst} shows the time evolution of the difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
+We can observe two obvious periods. 
+ In May 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets.
+ This situation means that before May 2013, the developers do not have enough time for a ticket.
+ It might constraint developers to not consider source code quality in the solution they provide for tickets.
+
+ A period after May 2013 the time estimated is superior to the time spent for evolution and defect tickets. 
  This estimate is improving for evolution tickets as the regression line is closing to 0.
-But for defects tickets the overestimation trend to increase.
+But for defects tickets, the overestimation tends to increase.
 
@@
 The developers' team is now using it and the software studied source code is now versioned.
-This opens the door for further analysis of the code repository to understand the system evolution. 
-Using the ticket database, the moving average and regression line, we build a defect model mainly assess the developer effort throughout the project life cycle.
-We will use this model to monitor our future actions which are: how to decompose the system big methods.
+This will open the door for further analysis specifically on the code repository to understand the system evolution. 
+By analysing the ticket database with  moving average and regression line, we  characterize the system.
+ This result will be used to monitor our future actions on the system.
 \bibliographystyle{plainnat}
 %\bibliographystyle{alpha}
-\bibliography{rmod,other,new}
+\bibliography{rmod,new}
 

### 2019-11-28 article.tex
integrate nicolas modifications

@@
 \usepackage{float}
-\usepackage[font=scriptsize]{caption}
+%\usepackage[font=scriptsize]{caption}
 \usepackage[sort&compress,square,comma,authoryear]{natbib}
@@
 To ensure the future of the system, and through it, of the company itself, some re-engineering actions might be necessary.
-The long period of growth and evolution of the systems as well as staff evolution, lead to problems such as dead code, duplicate code, and obsolete documentation. 
+The long period of growth and evolution of the system as well as staff evolution, lead to problems such as dead code, duplicate code, and obsolete documentation. 
 The developers at the origin of the application are no longer present, so a large part of the knowledge (and this at different levels of granularity) is scattered or lost.
@@
 Past literature often relied on historical data on the source code, for example
-cyclomatic complexity \cite{gill91}, or number of lines of code \cite{port18}.
+cyclomatic complexity \citep*{gill91}, or number of lines of code \citep*{port18}.
 In lack of a reliable software versioning system, we could not use these solutions.
@@
 \label{sec:related-work}
-Recently, research on mining software repositories has received much attention as it attempts to understand software evolution \cite{Zhan10a}.
+Recently, research on mining software repositories has received much attention as it attempts to understand software evolution \citep*{Zhan10a}.
 Software defect history and source code history are often used to monitor software maintenance or predict the system's quality. 
-For instance, software defect prediction using software repositories has already been extensively discussed in the literature as witnessed by many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
+For instance, software defect prediction using software repositories has already been extensively discussed in the literature as witnessed by many literature surveys: \citep*{Catal09,Hall12,Hoss17,Li19a,malh15}.
 %"intro": de quoi on va parler et pourquoi en parler ?
@@
 %Mining a software defect history helps to collect valuable information about the software life evolution. 
-%Software re-engineering monitoring should be supported by prediction models that predict the quality under control (\cite{Lenar17}).
+%Software re-engineering monitoring should be supported by prediction models that predict the quality under control (\citep*{Lenar17}).
 
@@
 But these solutions rely on the availability of source code history. 
-For example, \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
-\cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution to monitor maintenance.
+For example, \citep*{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
+\citep*{port18,Zhan10a} used software defect history and source code history to assess a system evolution to monitor maintenance.
 
@@
 
-\cite{Herz13a} propose to consider ticket database.
+\citep*{Herz13a} propose to consider ticket database.
 He reports that $33.8\%$ of the bugs studied among five open-source projects were misclassified.
-For this reason, other researchers try to automatically re-classify maintenance activities (e.g. \cite{Mock20a,Levin19a}).
+For this reason, other researchers try to automatically re-classify maintenance activities (e.g. \citep*{Mock20a,Levin19a}).
 
-%Other researchers considered ticket database to characterize a system. For instance, \cite{Levin19a} 
+%Other researchers considered ticket database to characterize a system. For instance, \citep*{Levin19a} 
 At the company, maintenance activities classification is more reliable because it drives the entire software evolution process.
@@
   \item The category of the ticket is fine-grained whereas we are only interested in evolution versus corrective tickets.
-  In our analysis, we recategorize the tickets according to some simple dictionary provided by the team manager.
-  \item Duration are registered in the following string format : \emph{//number\_of\_days//number\_of\_hours//number\_of\_minute//}.
-   For example \emph{//1j//2h//00//}  (one day two hours), is the same as \emph{//1 jour//2h//}.
-  Sometimes the format is not respected . For example \emph{5 jours } or \emph{5 g} is registered instead of \emph{//5j//00//00//}.
-  We create a simple  converter which covers all the cases and convert them into duration.
+  In our analysis, we recategorized the tickets according to some simple dictionary provided by the team manager.
+
+  \item Duration are registered in a free text format with some conventions.
+  As should be expected, the conventions were not always respected (e.g. ``5d'' or ``5days'') and there were typos.
+  We created a simple  converter which covers all the cases and convert them into numerical values.
 
@@
 
-For all the time questions, the tickets are grouped by month of creation and their value (for example time to close the ticket) are averaged for the month of creation.  
+For all the questions on time (for example time to close the tickets), the tickets are grouped by month of creation and their value are averaged for the month of creation.  
 We compute the data for our questions as follows:
@@
 
-  \item We compute the \emph{closing time} of a ticket simply as the time between creation and closing of each (closed) ticket.
+  \item We compute the \emph{closing time} of a ticket simply as the time between creation and closing.
+  This is only computed for closed tickets, the other ones are ignored.
 
-  \item  The time spent by the developers to implement its solution for a ticket is provided in the format (\emph{//number\_of\_days//number\_of\_hours//number\_of\_minute//}).
- We convert this format into duration for each tickets.
+  \item  The time spent by the developers to implement the solution for a ticket is recorded in a ``Time'' table related to the ticket.
+  We sum all ``Time'' rows linked to the ticket that are marked as development.
 
- \item The testing time is recorded in the ticket database in the format (\emph{//number\_of\_days//number\_of\_hours//number\_of\_minute//}).
-  We convert this information in duration.
+ \item The time spent by the developers to implement the solution for a ticket is recorded in a ``Time'' table, we sum all ``Time'' rows linked to the ticket that are marked as testing
 
- \item For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
- This estimation is based on the experience of the team manager.  
- We compute the difference  between the time spent by the developer and the estimation per month over the life cycle of the system.  
+ \item In the ticket there is a field recording the estimated time to solve it.
+ This field is filled by the team manager.
+ There is also a field recording the total time spent on the ticket by the developer.
+ We compute the difference  between the total time spent and the estimated time.
+ If this difference is positive, there was under estimation, and if it is negative there was over estimation.
  %autre metric
@@
 
-We then plotted the data simply on a 2 dimension graph, but we noticed a very large variation of the results (nonstationary results) that made it hard to interpret the graphs.
-To get smoother plots, we computed the moving average of [month-2; month+2] on each month.
-Therefore, plotted data for July 2010 of any time metric correspond to the average time of all tickets opened between May 2010 (inclusive) and September 2010 (inclusive).
+We finally plotted the data on a 2 dimension graph.
+We noticed a very large variation of the results from month to month (nonstationary results).
+This made it hard to interpret the graphs.
+To get smoother plots, we computed the moving average of [month - 2; month + 2] for each month.
+So for example, plotted data for July 2010 corresponds to the average time of all tickets opened between May 2010 (inclusive) and September 2010 (inclusive).
+We will also plot the linear regression of the curve for each graph to get a better notion of the trend.
 
-Finally, to get a better notion of the trend, we will also plot the linear regression of the curve for each graph.
-
-\subsection{Results}
+\section{Results}
 %-------------------------------------------------------------------------------
 
-\subsubsection{Souce code versionning}
+\subsection{Souce code versionning}
 %-------------------------------------------------------------------------------
@@
 
-\subsubsection{Data collection}
+\subsection{Data collection}
 %-------------------------------------------------------------------------------
@@
 We note that 56\% of defect tickets seems a high proportion.
-Literature (e.g. \cite{Pigo96a} ) states that the proportion is typically 20\% to 25\% of defect tickets.
+Literature (e.g. \citep*{Pigo96a} ) states that the proportion is typically 20\% to 25\% of defect tickets.
 This is an issue that we will investigate and monitor in the future.
 
-\subsubsection{Time to close a ticket}
+\subsection{Time to close a ticket}
 %-------------------------------------------------------------------------------
@@
 
-Figure \ref{fig:closingTime} presents the trend of closing time for evolution (up) and defect (down) tickets.
+Figure \ref{fig:closingTime} presents the values of closing time for evolution (up) and defect (down) tickets.
 One can notice a large variation of plotted time, even after smoothing it with the moving average. 
@@
 
-\subsubsection{Developer time spent on a ticket}
+\subsection{Developement time spent on a ticket}
 %-------------------------------------------------------------------------------
 
-When a developer works on a ticket, he spent time to analyze the task. 
-He then implements a solution and then tests.
- The time spent analyzing and implementing solution for the ticket depends on the workload of the ticket, the complexity of the system, etc.
+%The time spent analyzing and implementing solution for the ticket depends on the workload of the ticket, the complexity of the system, etc.
 
@@
   \includegraphics[width=70mm]{./images/devDefect.png}
-  \caption{Time spent by a developer to implement his solution for  evolution (up) and defect (down) tickets}
+  \caption{Time spent by developers to implement his solution for  evolution (up) and defect (down) tickets}
   \label{fig:devTimeDev}
@@
 %ressemble a closing time
-Figure \ref{fig:devTimeDev} presents the trend of closing time for evolution (up) and defect (down) tickets.
-As Figure \ref{fig:closingTime}, Figure \ref{fig:devTimeDev} show a large variation even after smoothing.
+Figure \ref{fig:devTimeDev} presents the time spent by developers to implement a solution to evolution (up) and defect (down) tickets.
+As Figure \ref{fig:closingTime}, Figure \ref{fig:devTimeDev} shows a large variation even after smoothing.
 
-It takes longer (on average) to implement a solution for an evolution ticket than a defect ticket which seems natural.
+It takes longer (on average) to implement a solution for an evolution ticket than a defect ticket. This seems natural.
 
 We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
-Finally, we note that the closing time over the 15 years was multiplied by 1.5 for evolution tickets and 4 for defect tickets.
-This is an issue to investigate.
-\subsubsection{Time  to test a ticket after development}
+Finally, we note that the time spent by developers to implement a solution was multiplied by a similar factor for evolution and defects (about 8 or 10).
+
+\subsection{Testing time by the developper}
 %-------------------------------------------------------------------------------
-
+\label{sec:testingTime}
 % constant pour defect -> OK
@@
 \end{figure}
-When a developer finishes a development related to a ticket, he tests his solution.  
-Figure \ref{fig:devTimeTest} presents the trend of the time spent by a developer to test his solution for evolution (up) and defect (down) tickets.
-We can observe that the time spent on testing evolution tickets is decreasing. 
-This might be because developers lack time to  test evolution tickets. 
-The lost of quality of the system and the growing number of defects in the system may be due to lack of tests.
-The time spent to test defects tickets is relatively constant which is ok.
 
-\subsubsection{Time estimation}
+%When a developer finishes a development related to a ticket, he tests his solution.  
+Figure \ref{fig:devTimeTest} presents the trend of the time spent by developers to test their solution for evolution (up) and defect (down) tickets.
+We can observe that the time is decreasing for evolution tickets and stable for defect tickets. 
+This might be due to a pressure to deliver new evolutions. We will come back to this in the next section.
+It is possible that this declining testing time results in a loss of quality of the system that could explain the results shown in the previous sections.
+
+\subsection{Time estimation}
  %-------------------------------------------------------------------------------
 
-%2 periodes tres claires en quelle annee et du a un effort explicite pour mieux evaluer le temps qui est maintenant fait en interne par la manager.
+%2 periodes tres claires en quelle annee et du a un effort explicitep* pour mieux evaluer le temps qui est maintenant fait en interne par la manager.
 
@@
     %The xAxis represent months from 2004 to 2019}
-    \caption{Difference between time spent by a developer  and time estimated for  evolution (up) and defect (down) tickets}
+    \caption{Difference between time spent by  developers and time estimated for  evolution (up) and defect (down) tickets}
   \label{fig:devEst}
@@
 
-Figure \ref{fig:devEst} shows the time evolution of the difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
-We can observe two obvious periods. 
- In May 2013 the time spent by the developer is superior to the time estimated with and increasing variation for evolution and defect tickets.
- This situation means that before May 2013, the developers do not have enough time for a ticket.
- It might constraint developers to not consider source code quality in the solution they provide for tickets.
+Figure \ref{fig:devEst} shows the  difference between the time spent by the developer and the time estimated for evolution (up) and defect (down) tickets.
+We can observe two obvious periods: before and after May 2013. 
+Before May 2013 the time spent by the developer is superior to the time estimated with and increasing difference for both evolution and defect tickets.
+This means that the developers did not have enough time to solve the tickets.
+It constrained developers in their task which might have impacted negatively the quality of the solutions and therefore of the code.
 
- A period after May 2013 the time estimated is superior to the time spent for evolution and defect tickets. 
+After May 2013 the time estimated is superior to the time spent for evolution and defect tickets. 
 This estimate is improving for evolution tickets as the regression line is closing to 0.
-But for defects tickets, the overestimation tends to increase.
+For defects tickets, the overestimation tends to increase.
+We could relate this to diminishing testing time (Section \ref{sec:testingTime}) for evolution ticket (that could be due to a lack of time) whereas the testing time remains constant for defect tickets which still enjoy a clear over-estimation.
+However, it must be noted that we did not see the same two periods difference in the previous section, therefore it is not clear that under-estimation of the time is at the source of the diminuing testing time.
 
@@
 
-In this paper, we present our first step in improving practices in a french company. We first introduce subversion, a version control system.
-The developers' team is now using it and the software studied source code is now versioned.
-This will open the door for further analysis specifically on the code repository to understand the system evolution. 
-By analysing the ticket database with  moving average and regression line, we  characterize the system.
- This result will be used to monitor our future actions on the system.
+In this paper, we present our first steps in improving practices in a medium company. We first introduced  a version control system in the evolution process.
+We chose Subversion as it seemed simpler to present to developpers that had no previous knowledge of versionning.
+The developement team is now using it and source code is now versioned.
+This will open the door for further analyses specifically on the code repository to understand the system evolution.
+
+As we want to monitor our future actions on the system, we analysed the ticket database to  characterize the current situation.
+The results seem to point to a declining quality of the system (it takes longer to implements tickets), but we also noted an imrovement in the estimation of the workload of a ticket.
+
 \bibliographystyle{plainnat}

### 2019-11-28 article.tex
fix grammatical mistakes

@@
 
-This is the situation at medium French company, which main business product we are studying.
+This is the situation at a medium French company, which main business product we are studying.
 The system is written in an old language (PowerBuilder) typically unknown to young programmers which translates in a difficulty to hire new developers.
@@
 \label{sec:related-work}
+
 Recently, research on mining software repositories has received much attention as it attempts to understand software evolution \citep*{Zhan10a}.
@@
 
-At the company, a ticket includes the following characteristics among other things:
-
 \begin{itemize}
@@
   \item time to analyze
-  \item time to implement solution
+  \item time to implement a solution
   \item time to test
@@
 
-  \item Duration are registered in a free text format with some conventions.
+  \item Durations are registered in a free text format with some conventions.
   As should be expected, the conventions were not always respected (e.g. ``5d'' or ``5days'') and there were typos.
-  We created a simple  converter which covers all the cases and convert them into numerical values.
+  We created a simple  converter which covers all the cases and converts them into numerical values.
 
@@
 For the reconstruction of the summarized source history, we already imported major versions sorted by release date until 2015 in an SVN repository. 
-At the end of the importing we could analyze changes between release at source code level.
+At the end of the importing, we could analyze changes between release at the source code level.
  %We then grouped them by major release. 
@@
 One can notice a large variation of plotted time, even after smoothing it with the moving average. 
-We don't see it as a pointing to a significant problem with the system.
+We don't see it as  pointing to a significant problem with the system.
 
@@
 We also note that the time is augmenting over the years for both categories which may be a sign of declining quality.
-Finally we note that the closing time over the 15 years was multiplied by 2 for evolution tickets and 3 for defect tickets.
+Finally, we note that the closing time over the 15 years was multiplied by 2 for evolution tickets and 3 for defect tickets.
 Again this is an issue to investigate.
@@
 We can observe that the time is decreasing for evolution tickets and stable for defect tickets. 
-This might be due to a pressure to deliver new evolutions. We will come back to this in the next section.
-It is possible that this declining testing time results in a loss of quality of the system that could explain the results shown in the previous sections.
+This might be due to the pressure to deliver new evolutions. We will come back to this in the next section.
+This declining testing time may result in a loss of quality of the system that could explain the results shown in the previous sections.
 
@@
 We could relate this to diminishing testing time (Section \ref{sec:testingTime}) for evolution ticket (that could be due to a lack of time) whereas the testing time remains constant for defect tickets which still enjoy a clear over-estimation.
-However, it must be noted that we did not see the same two periods difference in the previous section, therefore it is not clear that under-estimation of the time is at the source of the diminuing testing time.
+However, it must be noted that we did not see the same two periods difference in the previous section, therefore it is not clear that under-estimation of the time is at the source of the diminishing testing time.
 
@@
 In this paper, we present our first steps in improving practices in a medium company. We first introduced a version control system in the evolution process.
-We chose Subversion as it seemed simpler to present to developpers that had no previous knowledge of versionning.
-The developement team is now using it and source code is now versioned.
+We chose Subversion as it seemed simpler to present to developers that had no previous knowledge of versioning.
+The development team is now using it and the source code is now versioned.
 This will open the door for further analyses specifically on the code repository to understand the system evolution.
@@
 As we want to monitor our future actions on the system, we analysed the ticket database to characterize the current situation.
-The results seem to point to a declining quality of the system (it takes longer to implements tickets), but we also noted an imrovement in the estimation of the workload of a ticket.
-
+The results seem to point to the declining quality of the system (it takes longer to implements tickets), but we also noted an improvement in the estimation of the workload of a ticket.
 \bibliographystyle{plainnat}

### 2019-11-28 texlive_install.sh
Update texlive_install.sh

@@ -17,7 +17,8 @@ if ! command -v texlua > /dev/null; then
 
   # Install a minimal system
   ./install-tl --profile=../texlive/texlive.profile
-
+  sudo apt-get install texlive-fonts-recommended
+  
   cd ..
 fi
 
